### 2008-06-20 docs/paper/paper.tex
RPC seems to work now.
Have to implement it. Never mind the files under /www. Should've
excluded them, but, what the hell...

\documentclass{article}

\usepackage[english]{babel}
\usepackage{qtree}
\usepackage[utf8x]{inputenc}
\usepackage{linguex}

\author{Aleksandar Dimitrov}
\title{WERTi - Easing Second Language Acquisition}

\begin{document}
\maketitle

\tableofcontents

\section*{Preface}

\section{Introduction}

Using tools and methods made available through new achievements in computational
linguistics and related subjects like cognitive science to ease the process of
second language acquisition has only recently gained focus in research projects.
While adaptions of traditional data sources like dictionaries have been used for
quite a while we have yet to discover new and effective ways of

WERTi tries to approach this probmlem from a more general perspective. Making
use of the the momentum of the Internet, WERTi provides a platform for
implementing linguistic analysis and subsequent input enhancement methods on
user specified pages on the World Wide Web. Using Java Servlets technology for
serving content and the UIMA framework for processing it in a dynamic and
flexible session, we aim to provide a platform for linguistic processing of
online content that can go beyond input enhancement.

\subsection{Acknowledgements}

I'd like to thank my advisor \textsc{Detmar Meurers} for providing me with the
unique opportunity on working on the WERTi system. WERTi was originally thought
out and developed in Python by him and his team at the Ohio State University. My
job was to port the system he had already written to Java using UIMA and
generalize the concept as to make it easier to implement new functions.

I would also like to thank \textsc{Janina Radó}, who provided me with invaluable feedback
about the general style guidelines of papers of this kind.

Furthermore I'd like to thank , , , and for providing testing the system and for
their suggestions, remarks and feature requests.

\section{Explaining the Core Functionality}

\subsection{UIMA Analysis Engines}

The current processing line can be split up into three different parts that can
interact autonomously themselves but each depend on the output of their
predecessor. The components are arranged in the following manner:

\begin{itemize}

\item[HTML processing:] annotates HTML tags, finds ``relevant'' text within the
tags.

\item[Linguistic processing:] performs linguistic tasks (tokenization, sentence
boundary detection, part-of-speech tagging\ldots{}) on the text-annoatations
from the previous processing step.

\item[Post processing:] Performs all sorts of content enhancement on the
annotations of the previous two processing steps.

\end{itemize}

\subsubsection{HTML Processing}

The HTML processor method was designed to be primitive and efficient. While
using a fully capable HTML parser was considered, we preffered to use a more
simple approach since there didn't seem to be any need for the additional data
an HTML parser could have provided us with. Furthermore, changing the
implementation of an analysis step even this fundamental to further processing
should be easy and without side-effects as long as the requirements to
preconditions and postconditions are met.

\paragraph{Preconditions} We have a document represented as a singleton and
stored in the UIMA-CAS that is passed to the \verb#process(CAS)#-method of the
\verb#HTMLAnnotator#-class.

\subsubsection{Linguistic Processing}

\subsubsection{Post Processing - Input Enhancement}

\section{The User Inteface}

\subsection{Web Interface}

\subsection{Programming Interface}

\section{Conclusion}

\subsection{Loose Ends}

\end{document}

### 2008-06-20 src/org/werti/client/WERTiService.java

@@ -1,0 +1,7 @@
+package org.werti.client;
+
+import com.google.gwt.user.client.rpc.RemoteService;
+
+public interface WERTiService extends RemoteService {
+	public String process(String[] pipeline, String[] tags);
+}

### 2008-06-20 src/org/werti/client/WERTiServiceAsync.java

@@ -1,0 +1,8 @@
+package org.werti.client;
+
+import com.google.gwt.user.client.rpc.AsyncCallback;
+
+public interface WERTiServiceAsync {
+	@SuppressWarnings("unchecked")
+	public void process(String[] pipeline, String[] tags, AsyncCallback callback);
+}

### 2008-06-20 src/org/werti/client/WERTiUI.java

@@ -1,10 +1,16 @@
 package org.werti.client;
 
+import com.google.gwt.core.client.GWT;
+
 import com.google.gwt.user.client.Window;
 import com.google.gwt.user.client.WindowResizeListener;
 
+import com.google.gwt.user.client.rpc.AsyncCallback;
+import com.google.gwt.user.client.rpc.ServiceDefTarget;
+
 import com.google.gwt.user.client.ui.Button;
 import com.google.gwt.user.client.ui.CheckBox;
+import com.google.gwt.user.client.ui.ClickListener;
 import com.google.gwt.user.client.ui.Composite;
 import com.google.gwt.user.client.ui.FlowPanel;
 import com.google.gwt.user.client.ui.HTML;
@@ -18,11 +24,25 @@ import com.google.gwt.user.client.ui.Widget;
 
 public class WERTiUI extends Composite implements WindowResizeListener {
 
+	private static final String[] enhancementMethods = { "clr", "ask", "fib" };
+	private static final String[] enhancementNames = { "Colorize"
+			, "Click on the right word"
+			, "Fill in the blanks" };
+	private static final String defaultEnhancement = "clr";
+
+	private static final String[] posTags = { "NN", "IN", "DT" };
+	private static final String[] posNames = { "Nouns", "Prepositions", "Determiners" };
+	private static final String defaultTag = "IN";
+
+	private String[] pipeline = { "smp", "hmm", "hil" };
+	private String[] tags = { "NN" };
+
 	private static final String STYLE_PREFIX = "WERTi";
 	int windowWidth;
 
 	private VerticalPanel topPanel;
 	private TabPanel contentPanel;
+	private Button submitButton;
 	/**
 	 * Content wrapper. Put stuff here.
 	 */
@@ -57,16 +77,37 @@ public class WERTiUI extends Composite implements WindowResizeListener {
 		contentPanel.selectTab(0);
 	}
 
-	private static final String[] enhancementMethods = { "clr", "ask", "fib" };
-	private static final String[] enhancementNames = { "Colorize"
-			, "Click on the right word"
-			, "Fill in the blanks" };
-	private static final String defaultEnhancement = "clr";
+	private void error(String huh) {
+	
+	}
 
-	private static final String[] posTags = { "NN", "IN", "DT" };
-	private static final String[] posNames = { "Nouns", "Prepositions", "Determiners" };
-	private static final String defaultTag = "IN";
[…]

### 2008-06-20 src/org/werti/server/WERTiServiceImpl.java

@@ -1,0 +1,13 @@
+package org.werti.client;
+
+import com.google.gwt.user.server.rpc.RemoteServiceServlet;
+
+public class WERTiServiceImpl extends RemoteServiceServlet implements WERTiService {
+
+	public static final long serialVersionUID = 0;
+
+	public String process(String[] pipeline, String[] tags) {
+		return null;
+	}
+}
+

### 2008-06-20 src/org/werti/uima/ae/LingPipeTagger.java

@@ -25,26 +25,28 @@ public class LingPipeTagger extends JCasAnnotator_ImplBase implements Tagger {
 
 		final Iterator<SentenceAnnotation> sit = sentIndex.iterator();
 
-		while (sit.hasNext()) {
-			sentence.clear();
-			tlist.clear();
-			final SentenceAnnotation sa = sit.next();
-			Iterator<Token> tit = toknIndex.subiterator(sa);
-
-			// fill sentence
-			while (tit.hasNext()) {
-				final Token t = tit.next();
-				tlist.add(t);
-				sentence.add(new TaggedWord(t.getCoveredText()));
-			}
-
-			assert true: tlist.size() == sentence.size();
-			final int size = tlist.size();
-			for (int i = 0; i < size; i++) {
-				final Token t = tlist.get(i);
-				t.setTag(sentence.get(i).tag());
-			}
-		}
+/*
+ *                while (sit.hasNext()) {
+ *                        sentence.clear();
+ *                        tlist.clear();
+ *                        final SentenceAnnotation sa = sit.next();
+ *                        Iterator<Token> tit = toknIndex.subiterator(sa);
+ *
+ *                        // fill sentence
+ *                        while (tit.hasNext()) {
+ *                                final Token t = tit.next();
+ *                                tlist.add(t);
+ *                                sentence.add(new TaggedWord(t.getCoveredText()));
+ *                        }
+ *
+ *                        assert true: tlist.size() == sentence.size();
+ *                        final int size = tlist.size();
+ *                        for (int i = 0; i < size; i++) {
+ *                                final Token t = tlist.get(i);
+ *                                t.setTag(sentence.get(i).tag());
+ *                        }
+ *                }
+ */
 	}
 
 	public void initialize(UimaContext context) {

### 2008-06-21 src/org/werti/client/WERTi.java
RPCs are finally working.
YeAAAAAAHHH!

@@ -7,20 +7,30 @@ import com.google.gwt.dom.client.Document;
 import com.google.gwt.dom.client.HeadElement;
 import com.google.gwt.dom.client.LinkElement;
 
+import com.google.gwt.user.client.Window;
+import com.google.gwt.user.client.WindowResizeListener;
+
+import com.google.gwt.user.client.rpc.AsyncCallback;
+import com.google.gwt.user.client.rpc.ServiceDefTarget;
+
 import com.google.gwt.user.client.ui.Button;
+import com.google.gwt.user.client.ui.CheckBox;
 import com.google.gwt.user.client.ui.ClickListener;
 import com.google.gwt.user.client.ui.Composite;
 import com.google.gwt.user.client.ui.DialogBox;
+import com.google.gwt.user.client.ui.FlowPanel;
 import com.google.gwt.user.client.ui.HTML;
+import com.google.gwt.user.client.ui.HorizontalPanel;
 import com.google.gwt.user.client.ui.Label;
+import com.google.gwt.user.client.ui.RadioButton;
 import com.google.gwt.user.client.ui.RootPanel;
+import com.google.gwt.user.client.ui.SimplePanel;
+import com.google.gwt.user.client.ui.TabPanel;
+import com.google.gwt.user.client.ui.TextBox;
 import com.google.gwt.user.client.ui.VerticalPanel;
 import com.google.gwt.user.client.ui.Widget;
 
-/**
- * Entry point classes define <code>onModuleLoad()</code>.
- */
-public class WERTi implements EntryPoint {
+public class WERTi extends Composite implements WindowResizeListener, EntryPoint {
 
 	private Label styleTester;
 
@@ -47,10 +57,10 @@ public class WERTi implements EntryPoint {
 		RootPanel.get().add(styleTester);
 
 		// Create the constants
-		WERTiConstants constants = (WERTiConstants) GWT.create(WERTiConstants.class);
+		// WERTiConstants constants = (WERTiConstants) GWT.create(WERTiConstants.class);
 
 		// Create the User Interface
-		app = new WERTiUI();
+		app = new WERTi();
 
                 /*
 		 *setupTitlePanel(constants);
@@ -97,10 +107,220 @@ public class WERTi implements EntryPoint {
 		getHeadElement().appendChild(linkElem);
 	}
 
+
+	private static final String[] enhancementMethods = { "clr", "ask", "fib" };
[…]

### 2008-06-21 src/org/werti/client/WERTiService.java

@@ -3,5 +3,5 @@ package org.werti.client;
 import com.google.gwt.user.client.rpc.RemoteService;
 
 public interface WERTiService extends RemoteService {
-	public String process(String[] pipeline, String[] tags);
+	public String process(String[] pipeline, String[] tags, String url, String enhance);
 }

### 2008-06-21 src/org/werti/client/WERTiServiceAsync.java

@@ -4,5 +4,5 @@ import com.google.gwt.user.client.rpc.AsyncCallback;
 
 public interface WERTiServiceAsync {
 	@SuppressWarnings("unchecked")
-	public void process(String[] pipeline, String[] tags, AsyncCallback callback);
+	public void process(String[] pipeline, String[] tags, String url, String enhance, AsyncCallback callback);
 }

### 2008-06-21 src/org/werti/client/WERTiUI.java

@@ -1,211 +1,0 @@
-package org.werti.client;
-
-import com.google.gwt.core.client.GWT;
-
-import com.google.gwt.user.client.Window;
-import com.google.gwt.user.client.WindowResizeListener;
-
-import com.google.gwt.user.client.rpc.AsyncCallback;
-import com.google.gwt.user.client.rpc.ServiceDefTarget;
-
-import com.google.gwt.user.client.ui.Button;
-import com.google.gwt.user.client.ui.CheckBox;
-import com.google.gwt.user.client.ui.ClickListener;
-import com.google.gwt.user.client.ui.Composite;
-import com.google.gwt.user.client.ui.FlowPanel;
-import com.google.gwt.user.client.ui.HTML;
-import com.google.gwt.user.client.ui.HorizontalPanel;
-import com.google.gwt.user.client.ui.RadioButton;
-import com.google.gwt.user.client.ui.SimplePanel;
-import com.google.gwt.user.client.ui.TabPanel;
-import com.google.gwt.user.client.ui.TextBox;
-import com.google.gwt.user.client.ui.VerticalPanel;
-import com.google.gwt.user.client.ui.Widget;
-
-public class WERTiUI extends Composite implements WindowResizeListener {
-
-	private static final String[] enhancementMethods = { "clr", "ask", "fib" };
-	private static final String[] enhancementNames = { "Colorize"
-			, "Click on the right word"
-			, "Fill in the blanks" };
-	private static final String defaultEnhancement = "clr";
-
-	private static final String[] posTags = { "NN", "IN", "DT" };
-	private static final String[] posNames = { "Nouns", "Prepositions", "Determiners" };
-	private static final String defaultTag = "IN";
-
-	private String[] pipeline = { "smp", "hmm", "hil" };
-	private String[] tags = { "NN" };
-
-	private static final String STYLE_PREFIX = "WERTi";
-	int windowWidth;
-
-	private VerticalPanel topPanel;
-	private TabPanel contentPanel;
-	private Button submitButton;
-	/**
-	 * Content wrapper. Put stuff here.
-	 */
-	private SimplePanel contentWrapper;
-
-	/**
-	 * Constructs the layout and widegts of the application.
-	 */
-	public WERTiUI() {
-		FlowPanel layout = new FlowPanel();
-		initWidget(layout);
-
-		mkTopPanel();
[…]

### 2008-06-21 src/org/werti/server/WERTiServiceImpl.java

@@ -1,13 +1,241 @@
-package org.werti.client;
+package org.werti.server;
+
+import java.io.BufferedReader;
+import java.io.FileWriter;
+import java.io.IOException;
+import java.io.InputStreamReader;
+
+import java.net.MalformedURLException;
+import java.net.URL;
+import java.net.URLConnection;
+
+import java.util.Iterator;
+
+import java.util.logging.Level;
+import java.util.logging.Logger;
 
 import com.google.gwt.user.server.rpc.RemoteServiceServlet;
 
+import org.apache.uima.UIMAFramework;
+
+import org.apache.uima.analysis_engine.AnalysisEngine;
+
+import org.apache.uima.cas.FSIndex;
+
+import org.apache.uima.jcas.JCas;
+
+import org.apache.uima.jcas.cas.IntegerArray;
+import org.apache.uima.jcas.cas.StringArray;
+
+import org.apache.uima.resource.ResourceSpecifier;
+
+import org.apache.uima.util.InvalidXMLException;
+import org.apache.uima.util.XMLInputSource;
+
+import org.werti.client.WERTiService;
+
+import org.werti.uima.types.Enhancement;
+
 public class WERTiServiceImpl extends RemoteServiceServlet implements WERTiService {
+	private static final String PREFIX = "/var/local/resources/werti/descriptors/";
+	private static final String ENHNCE = PREFIX + "enhancers/PoSEnhancer.xml";
+	private static final String OPERTR = PREFIX + "operators/";
+
+
+	// maximum amount of of ms to wait for a web-page to load
+	private static final int MAX_WAIT = 1000 * 10;
+
+	private static final Logger log = Logger.getLogger("org.werti");
 
 	public static final long serialVersionUID = 0;
 
-	public String process(String[] pipeline, String[] tags) {
+	public String process(String[] pipeline, String[] tags, String url, String enhance) {
+		//DEBUG
+		log.setLevel(Level.ALL);
+
+		log.fine("Arguments, pipeline:");
+		for (String e:pipeline) {
+			log.fine(e);
+		}
+		log.fine("Arguments, tags");
+		for (String e:tags) {
+			log.fine(e);
+		}
+		log.fine("Arguments, url: "+url);
+
+		String descriptor = "";
+		for (String e:pipeline) {
+			descriptor += e + "-";
+		}
+		descriptor = OPERTR + descriptor.substring(0,descriptor.length()-1) + ".xml";
[…]

### 2008-06-21 web/org.werti.WERTi/org.werti.WERTi.nocache.js

@@ -1,0 +1,11 @@
+function org_werti_WERTi(){var l='',B='" for "gwt:onLoadErrorFn"',z='" for "gwt:onPropertyErrorFn"',Db='"><\/script>',n='/',ib='39FE9C074DB289A2327A3107714FACC1.cache.html',kb='502ED2B06E5060F8492AF7F3BCA53279.cache.html',mb='633215CA50C4A7023CEB43AD3F002F02.cache.html',jb='6BD6ADB94AA47D3183467BAD7B65CB6F.cache.html',Cb='<script id="',Ab="<script>org_werti_WERTi.onInjectionDone('org.werti.WERTi')<\/script>",v='=',y='Bad handler "',lb='D195A71DA430545575CEA9E62A25B8C9.cache.html',vb='DOMContentLoaded',Eb='SCRIPT',ub='WERTi.css',Bb='__gwt_marker_org.werti.WERTi',o='base',q='clear.cache.gif',u='content',db='gecko',eb='gecko1_8',nb='gwt.hybrid',ob='gwt/standard/standard.css',A='gwt:onLoadErrorFn',w='gwt:onPropertyErrorFn',t='gwt:property',tb='head',hb='hosted.html?org_werti_WERTi',sb='href',bb='ie6',wb='iframe',p='img',xb="javascript:''",pb='link',r='meta',gb='moduleRequested',ab='msie',s='name',D='opera',m='org.werti.WERTi',zb='position:absolute;width:0;height:0;border:none',qb='rel',F='safari',yb='selectionDone',cb='selectionStart',x='startup',rb='stylesheet',fb='unknown',C='user.agent',E='webkit';var ac=window,k=document,ic=ac.external,Fb=ac.__gwtstatsEvent?function(a,b,c,d){ac.__gwtstatsEvent(a,b,c,d)}:null,vc,lc,fc,ec=l,oc={},yc=[],uc=[],dc=[],rc,tc;Fb&&Fb(m,x,cb,{millis:(new Date()).getTime()});if(!ac.__gwt_stylesLoaded){ac.__gwt_stylesLoaded={}}if(!ac.__gwt_scriptsLoaded){ac.__gwt_scriptsLoaded={}}function kc(){try{return ic&&(ic.gwtOnLoad&&ac.location.search.indexOf(nb)==-1)}catch(a){return false}}
[…]

### 2008-06-23 docs/paper/abstract.tex
started Abstract. Changes to interface.
Now everything seems to work.

\documentclass[a4paper,twocolumn]{scrartcl}

\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage{aleks}
\usepackage{qtree}
\usepackage{linguex}

\author{Aleksandar Dimitrov}
\title{Rebuilding WERTi: Providing a Platform for Aiding Second Language Acquisition}

\begin{document}

\maketitle

In the course of this presentation I want to provide insight into the
development process of my re-implementation of WERTi, a system to aid second
language acquisition of adult learners. The original implementation of WERTi was
capable of requesting news articles from a certain news web
site\footnote{\texttt{http://www.reuters.com}} and perform different kinds of
input enhancements on it.

While the original implementation was written in the programming language
\emph{Python}, this new design is rooted in \emph{Java} technologies and makes
use of several frameworks:
\begin{itemize}
  \item UIMA - IBM's \emph{Unstructured Information Management Architecture},
    used to process web contents, find natural
    language and annotate it according to its linguistic features.
  \item Java Servlets and Server Pages - for hosting the web content and
    executing server side processing.
  \item GWT - The \emph{Google Web Toolkit}. This technology compiles native
    \emph{Java} code to \emph{JavaScript} which is then executed on the client
    side. It also eases the process of integrating Remote Procedure Calls to
    communicate between server and client side.
\end{itemize}

The new \emph{Java} implementation now supports arbitrary web sites as inputs,
multiple languages and has some new features regarding input enhancement.
Overall the development focus rested on providing a flexible platform that can be
easily extended to include more functionality. UIMA is used on the server side
to provide a flexible analysis framework and GWT, on the client side, provides
an easy way to enrich content of web pages.

\end{document}

### 2008-06-23 src/org/werti/client/Application.java

@@ -1,0 +1,272 @@
+package org.werti.client;
+
+import com.google.gwt.core.client.GWT;
+
+import com.google.gwt.user.client.Window;
+import com.google.gwt.user.client.WindowResizeListener;
+
+import com.google.gwt.user.client.rpc.AsyncCallback;
+import com.google.gwt.user.client.rpc.ServiceDefTarget;
+
+import com.google.gwt.user.client.ui.Button;
+import com.google.gwt.user.client.ui.CheckBox;
+import com.google.gwt.user.client.ui.ClickListener;
+import com.google.gwt.user.client.ui.Composite;
+import com.google.gwt.user.client.ui.FlowPanel;
+import com.google.gwt.user.client.ui.HTML;
+import com.google.gwt.user.client.ui.HorizontalPanel;
+import com.google.gwt.user.client.ui.RadioButton;
+import com.google.gwt.user.client.ui.TabPanel;
+import com.google.gwt.user.client.ui.TextBox;
+import com.google.gwt.user.client.ui.VerticalPanel;
+import com.google.gwt.user.client.ui.Widget;
+
+public class Application extends Composite implements WindowResizeListener {
+
+	public class CRadioButton extends RadioButton implements isUseful {
+		private String canonicalValue;
+
+		public String getCanonicalValue() { return canonicalValue; }
+
+		public CRadioButton(String group, String text, String cv) {
+			super(group, text);
+			this.canonicalValue = cv;
+		}
+	}
+
+	public class CCheckBox extends CheckBox implements isUseful {
+		private String canonicalValue;
+
+		public String getCanonicalValue() { return canonicalValue; }
+
+		public CCheckBox(String text, String cv) {
+			super(text);
+			this.canonicalValue = cv;
+		}
+	}
+
+	public interface isUseful {
+		public boolean isChecked();
+		public String getCanonicalValue();
+	}
+
+	private static final String[] enhancementMethods = { "clr", "ask", "fib" };
+	private static final String[] enhancementNames = { "Colorize"
+			, "Click on the right word"
+			, "Fill in the blanks" };
+	private String defaultEnhancement = "clr";
+
+	private static final String[] posTags = { "NN", "IN", "DT" };
+	private static final String[] posNames = { "Nouns", "Prepositions", "Determiners" };
[…]

### 2008-06-23 src/org/werti/client/WERTi.java

@@ -1,36 +1,26 @@
 package org.werti.client;
 
+
 import com.google.gwt.core.client.EntryPoint;
-import com.google.gwt.core.client.GWT;
 
 import com.google.gwt.dom.client.Document;
 import com.google.gwt.dom.client.HeadElement;
 import com.google.gwt.dom.client.LinkElement;
 
-import com.google.gwt.user.client.Window;
-import com.google.gwt.user.client.WindowResizeListener;
 
-import com.google.gwt.user.client.rpc.AsyncCallback;
-import com.google.gwt.user.client.rpc.ServiceDefTarget;
 
 import com.google.gwt.user.client.ui.Button;
-import com.google.gwt.user.client.ui.CheckBox;
 import com.google.gwt.user.client.ui.ClickListener;
 import com.google.gwt.user.client.ui.Composite;
 import com.google.gwt.user.client.ui.DialogBox;
-import com.google.gwt.user.client.ui.FlowPanel;
 import com.google.gwt.user.client.ui.HTML;
-import com.google.gwt.user.client.ui.HorizontalPanel;
 import com.google.gwt.user.client.ui.Label;
-import com.google.gwt.user.client.ui.RadioButton;
 import com.google.gwt.user.client.ui.RootPanel;
 import com.google.gwt.user.client.ui.SimplePanel;
-import com.google.gwt.user.client.ui.TabPanel;
-import com.google.gwt.user.client.ui.TextBox;
 import com.google.gwt.user.client.ui.VerticalPanel;
 import com.google.gwt.user.client.ui.Widget;
 
-public class WERTi extends Composite implements WindowResizeListener, EntryPoint {
+public class WERTi implements EntryPoint {
 
 	private Label styleTester;
 
@@ -60,7 +50,7 @@ public class WERTi extends Composite implements WindowResizeListener, EntryPoint
 		// WERTiConstants constants = (WERTiConstants) GWT.create(WERTiConstants.class);
 
 		// Create the User Interface
-		app = new WERTi();
+		app = new Application();
 
                 /*
 		 *setupTitlePanel(constants);
@@ -69,26 +59,6 @@ public class WERTi extends Composite implements WindowResizeListener, EntryPoint
 		 *setupMainMenu(constants);
                  */
 		RootPanel.get().add(app);
-
-
-		// Create the dialog box
-		final DialogBox dialogBox = new DialogBox();
[…]

### 2008-06-26 docs/paper/paper.tex
Post-Presentation commit
Various updates. WERTi will be restructured significantly this weekend.

@@
 \usepackage{qtree}
+\usepackage{aleks}
 \usepackage[utf8x]{inputenc}
@@
 
+This section will explain the principles underlying WERTi's functionality by
+first looking at the data processing architecture and then showing how this is
+then integrated into the user interface of the web application.
+
 \subsection{UIMA Analysis Engines}
@@
 The current processing line can be split up into three different parts that can
-interact autonomously themselves but each depend on the output of their
-predecessor. The components are arranged in the following manner:
+interact autonomously but each depend on the output of their predecessor. The
+components are arranged in the following order:
 
@@
 \item[HTML processing:] annotates HTML tags, finds ``relevant'' text within the
-tags.
+tags. This lays ground to later linguistic analysis by setting the margins of
+where the latter has to operate on in the web content.
 
 \item[Linguistic processing:] performs linguistic tasks (tokenization, sentence
-boundary detection, part-of-speech tagging\ldots{}) on the text-annoatations
-from the previous processing step.
+boundary detection, part-of-speech tagging\ldots{}) on the text-annotations
+from the previous processing step. This is also the most intensive step from a
+computational point of view. Optimizations to the code are most likely to yield
+visible results here.
 
 \item[Post processing:] Performs all sorts of content enhancement on the
-annotations of the previous two processing steps.
+annotations of the previous two processing steps. Note that this step depends on
+both annotation results: it also needs certain HTML markups in order to
+correctly organize all of the code that is going to be executed on client side.
 
 \end{itemize}
+
+We will now go on and explain those steps in further detail.
 
@@
 The HTML processor method was designed to be primitive and efficient. While
-using a fully capable HTML parser was considered, we preffered to use a more
-simple approach since there didn't seem to be any need for the additional data
-an HTML parser could have provided us with. Furthermore, changing the
+using a fully capable HTML parser was considered, we preferred to use a more
+simple approach. Full and formally correct HTML markup was deemed unnecessary and
+too time intensive.
+Furthermore, changing the
 implementation of an analysis step even this fundamental to further processing
@@
 
-\paragraph{Preconditions} We have a document represented as a singleton and
+\paragraph{Preconditions} We have a document represented as a singleton
+String\footnote{As usual in UIMA. For large documents, UMIA provides ways of
+splitting up documents and processing the chunks independently. However, UIMA
+only considers documents well beyond one megabyte to be ``big enough'' to be
+split and the plain HTML most web pages serve rarely exceeds this mark.}   and
 stored in the UIMA-CAS that is passed to the \verb#process(CAS)#-method of the
 \verb#HTMLAnnotator#-class.
+\paragraph{Postconditions} The document contains annotations marking up the
+positions and spans of html tags in the document text. The names of
+tags\footnote{E.g. ``p'' for the tag \texttt{<p>} or ``div'' for the dag
+\texttt{div}.} are
+also stored and a \verb#isClosing#-flag is set, that denotes whether this tag is
+closing another\footnote{A preceding slash in the tag name closes the tag.}.
 
@@
 
+Linguistic processing goes through 3 major steps: \emph{Tokenization},
+\emph{Sentence Boundary Detection}
+
 \subsubsection{Post Processing - Input Enhancement}
 
-\section{The User Inteface}
+\section{The User Interface}
 
@@
 \subsection{Programming Interface}
+
+\section{The Development Process}
+In this section I want to display in what environment the project has been
+written and what technologies have been put to use.
+
+\subsection{Concept \& Design}
+The original design of WERTi has been developed at Ohio State University by
+\textsc{Detmar Meurers} and his research associates. There exist several papers
+about this original work. At Tübingen University the concept has been extended
+to
+
+\subsection{Design Process} My Work on the Java implementation of WERTi was
+mostly autonomous. I had been given free choice over the frameworks and
+development environment I wanted to put to use, with the only exceptions being
+being using \emph{Java} and the UIMA architecture to achieve maximum flexibility
+and portability. Maximum flexibility and extensibility were the main goals of
+the re-implementation.
+
+Development happened in a very productive atmosphere with weekly project
+meetings where core functionality and the design of the analysis process were
+discussed. After those most important aspects of the system were implemented, I
+continued work on the interface and extension of the analysis process mostly
+alone for organizational reasons.
+
+I chose to use mostly standard UNIX command line tools for writing, testing and
+debugging the code, although more advanced solutions like the Eclipse Java IDE
+were also used - mostly for easier organization of the work with the different
+frameworks\footnote{Especially UIMA which comes with a number
 

### 2008-06-26 docs/paper/pres.tex
Post-Presentation commit
Various updates. WERTi will be restructured significantly this weekend.

\documentclass{beamer}

\mode<beamer>{
\usetheme{Singapore}
%Berlin
%\usecolortheme{rose}
}

\usepackage[english]{babel}
\usepackage{qtree}
\usepackage{ucs}
\usepackage[utf8x]{inputenc}
\usepackage{amsfonts,amsmath}
\usepackage{linguex}
\usepackage{color}
\title{Rebuilding WERTi: Providing a Platform for Aiding Second Language Acquisition}
\institute{Universität Tübingen}
\author{Aleksandar L. Dimitrov}

\begin{document}

\begin{frame}
  \titlepage
\end{frame}

\begin{frame}
  \frametitle{Outline}
  \tableofcontents
\end{frame}

\section{What is WERTi?}

\subsection{Second Language Acquisition}
\begin{frame}
  \frametitle{Computational Methods in Second Language Acquisition}
  Make use of existing methods in computational linguistics and natural language
  processing\pause
  \begin{itemize}
    \item Increase the learner's awareness of grammatical patterns\ldots{}\pause
    \item \ldots{} trough input enhancement\pause\emph{ (Receptive Presentation) }\pause
    \item \ldots{} interaction with text in the target language\pause
      \begin{itemize}
	\item \emph{Productive Presentation/Perceiving Interaction}\pause
	\item \emph{Controlled Practice/Productive Interaction}\pause
      \end{itemize}
  \end{itemize}
  Leave room for new ideas.\pause
\end{frame}

\subsection{WERTi aids Second Language Acquisition}
\begin{frame}
  \frametitle{WERTi aids Second Language Acquisition}
  WERTi \ldots
  \begin{itemize}
    \item \ldots{} lets the user decide what content they want to see\pause\\
      $\to$ Would a restriction on the input texts be commendable?\pause
    \item \ldots{} provides example implementations of \emph{Receptive Presentation},
      \emph{Productive Presentation} and \emph{Controlled Practice}\pause
    \item \ldots{} is interactive and easily accessible to the user\pause
    \item \ldots{} has been re-written with flexibility in mind, in order to be
      extended by programmers\pause
  \end{itemize}
\end{frame}

\section{Working on WERTi}
\begin{frame}
  \frametitle{Working on WERTi}
  \begin{itemize}
    \item Complete rewrite, using new technologies\pause
    \item Acquisition of technologies proved a great challenge\pause
    \item Weekly design discussions greatly improved the overall designs
    \item Development by one person\pause
      \begin{itemize}
	\item Advantage: greater consistency, rapid prototyping\pause
	\item Disadvantages: fewer resources/capacity, possibility of creating a ``code bomb''\pause
      \end{itemize}
  \end{itemize}
\end{frame}
\subsection{The Goals}
\begin{frame}
  \frametitle{The Goals}
  \begin{itemize}
    \item Make linguistic processing more flexible\pause\\
      $\to$ using UIMA, the Unstructured Information Management Architecture\pause
    \item Provide server $\leftrightarrow$ client side interaction\pause\\
      $\to$ using RPC calls and GWT, the Google Web Toolkit\pause
    \item Extend possible targets to include (possibly) arbitrary web
      content\pause\\
      $\to$ Using heuristics and eventually linguistic methods to extract
      text\pause
    \item Overall:\pause\\
      $\to$ Provide an easy to extend web based platform to aid second language
      acquisition of adult learners
  \end{itemize}
\end{frame}

\section{Architecture}
\begin{frame}
  \frametitle{Architecture}
  WERTi is now modular:
  \begin{itemize}
    \item Two client side code modules,\pause
      \begin{itemize}
	\item one for the application interface\pause
	\item one for the enhancements interface\pause
    \item Server side code and\pause
    \item with in the server side code, linguistic analysis components\pause
  \end{itemize}
\end{frame}
\begin{frame}
  \frametitle{The general Picture}
  (Picture)
\end{frame}
\begin{frame}
  \frametitle{Textual and Linguistic Analysis}
  \begin{itemize}
    \item HTML tag recognition\pause
    \item Classification into relevant chunks of input\pause
    \item Tokenization\pause
    \item Sentence Boundary detection and coherence analysis\pause
    \item Part of Speech Tagging using different taggers\pause
    \item Enhancement Annotations\pause
  \end{itemize}
\end{frame}

\section{Conclusion/The Current Status} \subsection{Feature Proposals}
\begin{frame}
  \frametitle{The Current Status}
  \begin{itemize}
    \item WERTi is largely usable with a few bugs in the processing code (mostly
      HTML sanitization)\pause
    \item The user interface is not yet functional, but we have basic
      functionality\pause
    \item linguistic processing is so far feature complete, stable and
      fast\pause
    \item WERTi needs stress tests with many users to prove its
      scalability\pause
  \end{itemize}
\end{frame}
\begin{frame}
  \frametitle{Feature Proposals}
  \begin{itemize}
    \item A passivator\pause
    \item Partial translation (when ``mousing over'' a word)\pause
    \item Lemmatization could provide fill-in-the-blanks for finite forms\pause
    \item Phrase structures could be parsed and annotated\pause
    \item \ldots{}
  \end{itemize}
\end{frame}
\end{document}

### 2008-06-26 src/org/werti/client/Application.java

@@ -113,7 +113,7 @@ public class Application extends Composite implements WindowResizeListener {
 			public void onClick(Widget sender) {
 				WERTiServiceAsync wertiService = (WERTiServiceAsync) GWT.create(WERTiService.class);
 				ServiceDefTarget endpoint = (ServiceDefTarget) wertiService;
-				String moduleRelativeURL = GWT.getModuleBaseURL() + "/org.werti.WERTi/WERTiService";
+				String moduleRelativeURL = GWT.getHostPageBaseURL() + "/org.werti.WERTi/WERTiService";
 				endpoint.setServiceEntryPoint(moduleRelativeURL);
 				AsyncCallback callback = new AsyncCallback() {
 					public void onSuccess(Object result) {

### 2008-06-26 src/org/werti/client/Enhancements.java

@@ -1,0 +1,62 @@
+package org.werti.client;
+
+import com.google.gwt.core.client.EntryPoint;
+
+import com.google.gwt.user.client.DOM;
+import com.google.gwt.user.client.Element;
+
+import com.google.gwt.user.client.ui.HTML;
+import com.google.gwt.user.client.ui.KeyboardListener;
+import com.google.gwt.user.client.ui.RootPanel;
+import com.google.gwt.user.client.ui.TextBox;
+import com.google.gwt.user.client.ui.Widget;
+
+public class Enhancements implements EntryPoint {
+	public static final String PREFIX = "WERTi-span-";
+	Element e;
+	RootPanel trp;
+	public void onModuleLoad() {
+		for (int i = 0; ; i++) {
+			e = DOM.getElementById(PREFIX+i);
+			trp = RootPanel.get(PREFIX+i);
+			if (e == null) { break; }
+			final String word = e.getNodeValue();
+			e.setNodeValue("");
+			TextBox tb = new TextBox();
+			tb.setWidth((10*word.length())+"pt");
+		}
+	}
+
+	private class BlankListener implements KeyboardListener {
+		TextBox next;
+		String word;
+		String id;
+		public BlankListener(String word, String id) {
+			this.id = id;
+			this.word = word;
+		}
+
+		public void setNext(TextBox next) {
+			this.next = next;
+		}
+		
+		public void onKeyDown(Widget w, char key, int i) {
+		}
+
+		public void onKeyPress(Widget w, char key, int i) {
+			if (w instanceof TextBox) {
+				TextBox tb = (TextBox) w;
+				if (tb.getText().equals(word)) {
+					w.setVisible(false);
+					RootPanel.get(id).add(new HTML("<font color=\"#00FF00\">"+word+"</font>"));
+					if (next != null) {
+						next.setFocus(true);
+					}
+				} 
+			}
+		}
+
+		public void onKeyUp(Widget w, char key, int i) {
+		}
+	}
+}

### 2008-06-26 src/org/werti/client/EnhancementsService.java

@@ -1,0 +1,7 @@
+package org.werti.client;
+
+import com.google.gwt.user.client.rpc.RemoteService;
+
+public interface EnhancementsService extends RemoteService {
+
+}

### 2008-06-26 src/org/werti/client/EnhancementsServiceAsync.java

@@ -1,0 +1,5 @@
+package org.werti.client;
+
+public interface EnhancementsServiceAsync extends EnhancementsService {
+
+}

### 2008-06-26 src/org/werti/client/Gonfig.java

@@ -1,0 +1,2 @@
+package org.werti.client;
+

### 2008-06-26 src/org/werti/client/WERTi.java

@@ -59,8 +59,6 @@ public class WERTi implements EntryPoint {
 		 *setupMainMenu(constants);
                  */
 		RootPanel.get().add(app);
-
-		RootPanel.get().add(mainPanel);
 	}
 
 	/**

### 2008-06-26 src/org/werti/server/WERTiServiceImpl.java

@@ -211,7 +211,7 @@ public class WERTiServiceImpl extends RemoteServiceServlet implements WERTiServi
 		int skew = docText.indexOf("<head");
 		skew = docText.indexOf('>',skew)+1;
 
-		final String basetag = "<base href=\"" + baseurl + "\" />";
+		final String basetag = "<base href=\"" + baseurl + "\" /><script type=\"text/javascript\" language=\"javascript\" src=\"http://localhost:8888/WERTi/org.werti.Enhancements-xs.nocache.js\"></script><meta name='gwt:module' content='org.werti.Enhancements'/>";
 		rtext.insert(skew, basetag);
 		skew = basetag.length();
 

### 2008-06-26 src/org/werti/uima/enhancer/PoSEnhancer.java

@@ -59,6 +59,40 @@ public class PoSEnhancer extends JCasAnnotator_ImplBase {
 		return "WERTi-span-" + id;
 	}
 
+	@SuppressWarnings("unchecked")
+	private static void fibnew(JCas cas, String[] tags, UimaContext context) {
+		final FSIndex textIndex = cas.getAnnotationIndex(Token.type);
+		final Iterator<Token> tit = textIndex.iterator();
+
+		Token t = tit.next();
+
+		iteratetokens: while (tit.hasNext()) {
+			if (t.getTag() == null) {
+				context.getLogger().log(Level.WARNING,
+						"Encountered token with NULL tag");
+				tit.next();
+				continue iteratetokens;
+			}
+			if (arrayContains(t.getTag(), tags)) {
+				final Enhancement e = new Enhancement(cas);
+				e.setBegin(t.getBegin());
+				e.setEnd(t.getEnd());
+				final StringArray  sa = new StringArray(cas, 2);
+				final IntegerArray ia = new IntegerArray(cas, 2);
+
+				id++;
+				sa.set(0, "<span id=\"" + get_id() + "\">");
+				sa.set(1, "</span>");
+
+				ia.set(0, e.getBegin());
+				ia.set(1, e.getEnd());
+				e.setEnhancement_list(sa);
+				e.setIndex_list(ia);
+				e.addToIndexes();
+			}
+			t = tit.next();
+		}
+	}
 	// put annotations for FIB enhancement in the CAS
 	@SuppressWarnings("unchecked")
 	private static void fib(JCas cas, String[] tags, UimaContext context) {

### 2008-06-27 docs/paper/paper.tex
Tokenizer hyphen fix.
Hyphens were stubbornly marked as prepositions. God knows why.

--- 2008-06-20 docs/paper/paper.tex
@@
-\documentclass{article}
+\documentclass[12pt]{article}
 
@@
 
-\section*{Preface}
-
 \section{Introduction}
@@
 Using tools and methods made available through new achievements in computational
-linguistics and related subjects like cognitive science to ease the process of
-second language acquisition has only recently gained focus in research projects.
-While adaptions of traditional data sources like dictionaries have been used for
-quite a while we have yet to discover new and effective ways of
+linguistics and related subjects to ease the process of second language
+acquisition has only recently gained focus in research projects.  While
+digitalized versions of traditional data sources like dictionaries have already
+experienced usage to some extent already, we have yet to discover new and
+effective ways of aiding second language acquisition of adult learners. Many
+systems have so far been proposed and their implementations vary in quality and
+focus.
 
-WERTi tries to approach this probmlem from a more general perspective. Making
+WERTi tries to approach this probmlem from a general perspective. Making
 use of the the momentum of the Internet, WERTi provides a platform for
 implementing linguistic analysis and subsequent input enhancement methods on
-user specified pages on the World Wide Web. Using Java Servlets technology for
+user specified pages on the World Wide Web. Using Java Servlet and AJAX technology for
 serving content and the UIMA framework for processing it in a dynamic and
-flexible session, we aim to provide a platform for linguistic processing of
+flexible manner, we aim to provide a platform for linguistic processing of
 online content that can go beyond input enhancement.
 
-\subsection{Acknowledgements}
+\subsection{Concept \& Design}
 
-I'd like to thank my advisor \textsc{Detmar Meurers} for providing me with the
-unique opportunity on working on the WERTi system. WERTi was originally thought
-out and developed in Python by him and his team at the Ohio State University. My
-job was to port the system he had already written to Java using UIMA and
-generalize the concept as to make it easier to implement new functions.
+The original design of WERTi has been developed at Ohio State University by
+\textsc{Detmar Meurers} and his research associates. 
+%% TODO: not only detmar. Who else?
+There exist several papers
+about this original work. 
+%% TODO: Citation Needed
 
-I would also like to thank \textsc{Janina Radó}, who provided me with invaluable feedback
-about the general style guidelines of papers of this kind.
+At Tübingen University the concept has now been extended
+to encompass a wider range of functionality and provide a more scalable
+solution. To achieve this, several enterprise grade technologies have been put to
+use. Although this comes with certain drawbacks (such as an increase in the
+code base by as much as over 1000\%), they provided us with a more flexible and robust
+architecture which should be able to cope with most demands to the system.
 
-Furthermore I'd like to thank , , , and for providing testing the system and for
-their suggestions, remarks and feature requests.
+%\subsection{Acknowledgements}
 
-\section{Explaining the Core Functionality}
+%I'd like to thank my advisor \textsc{Detmar Meurers} for providing me with the
+%unique opportunity on working on the WERTi system. WERTi was originally thought
+%out and developed in Python by him and his team at the Ohio State University. My
+%job was to port the system he had already written to Java using UIMA and
+%generalize the concept as to make it easier to implement new functions.
 
-\subsection{UIMA Analysis Engines}
+%I would also like to thank \textsc{Janina Radó}, who provided me with invaluable feedback
+%about the general style guidelines of papers of this kind.
 
-The current processing line can be split up into three different parts that can
-interact autonomously themselves but each depend on the output of their
-predecessor. The components are arranged in the following manner:
+%Furthermore I'd like to thank , , , and for providing testing the system and for
+%their suggestions, remarks and feature requests.
+
+\section{The Development Process}
+
+In this section we will first explain the goals of the reimplementation and then
+display in what environment the project has been written and what technologies
+have been put to use.
+
+\subsection{Goals of the New Ipmlementation}
+
+ While the original implementation was
+ written in the programming language
+ Python, our new design is rooted in Java
+ technologies and makes use of several frameworks to ensure maximum scalability.
+
+The new system was written with several aspects in mind:
+\begin{itemize}
+  \item While the original system was restricted to a few hand picked web sites
+    and in fact only supporting input from one particular news
+    site\footnote{This site was \texttt{http://www.reuters.com}}, the new system
+    should be able to support almost arbitrary input from sites in the World
+    Wide Web. For this the system has to perform reliable and robust evaluation
+    of the site content in order filter out text for later natural language
+    processing tasks. This way we can provide the user with free choice over the
+    target material %% YAY!
+  \item Processing of site content should be generalized and made to be as
+    flexible as possible in order to ensure maximum extensibility of the
+    system. This also implied splitting up different parts of natural
+    language 
+    processing tasks on the input into several interdependent steps. This way,
+    the results of one of the \emph{Analysis Engines} can always serve as the
+    input to other engines.
+  \item Ensure asynchronous client $\leftrightarrow$ server communication capabilities in
+    order to allow evaluation of the user's performance on target texts.
+    Together with an anticipated user account system this would provide us with
+    the ability of measuring of a particular user's progress and provide them
+    with automated feedback on their abilities.
+  \item Overall we wanted to provide an easy to use, flexible and scalable web 
+    based platform for methods of second
+    language acquisition assistance.
+\end{itemize}
+
+\subsection{Design Process} The work on the Java implementation of WERTi happened
+mostly autonomous and was conducted by one person. Given free choice over the
+development environment and frameworks, a considerable part of the writing
+process was spent on evaluation and study of the technologies put to use. The
+only notable specifications set on the development environment was the use of
+UIMA, which in turn implied the use of the Java programming language.
+
+Development happened in a very productive atmosphere with mostly weekly project
+meetings between the programmer and the project supervisor where core
+functionality and the design of the analysis process were discussed. During the
+course of the design process, the system was several times restructured and some
+parts of it have by now been rewritten two or even three times.
+
+Work on the code has been mostly performed using standard UNIX command line
+tools for writing, testing and debugging code, although more advanced solutions
+like the Eclipse Java IDE were also used. They mostly provided easier
+organization of the work within the different frameworks\footnote{Most
+importantly UIMA which comes with a number of useful plugins to easily devise
+analysis engine outlines.}. All of the work has been tracked with a version
+control\footnote{The author chose to use the \emph{git} version control system,
+which has been and developed for and successfully used in the context of much greater
+codebases, such as the Linux kernel.} system on which further work on the system
+will also depend.
+
+\section{The Architecture of the System}
+
+This section will explain the principles underlying WERTi's functionality by
+first looking at the data processing architecture and then showing how it is
+integrated into the user interface of the web application.
+
+\subsection{The UIMA Analysis Engines}\label{sec:UIMA}
+
+All text extraction and natural language processing work is done inside the UIMA
+architecture.  Modifications  to the document's structure are clearly seperated
+from the process of annotating it. In this way we can ensure natural language
+analysis to be a consistent process on one and the same input.
+
+The NLP routines only add annotations to the document, and they are not supposed
+to change its state in any other way. Enriching the content of the web site is
+then left to an outside module that processes only the annotations and does not
+look at the document text itself. To achieve this degree of encapsulation
+between the different tasks, the system has been split into three main parts,
+operating independently:
 
@@
 
-\item[HTML processing:] annotates HTML tags, finds ``relevant'' text within the
-tags.
+\item{ HTML processing: }
 
-\item[Linguistic processing:] performs linguistic tasks (tokenization, sentence
-boundary detection, part-of-speech tagging\ldots{}) on the text-annoatations
-from the previous processing step.
+  During initial processing of the input text, which at this stage consists of
+  the raw web site content retrieved by the server,  HTML tag annotations are
+  made to distinguish HTML tags as non-natural language text. Then another
+  module finds ``relevant'' text within the text surrounded by tags. This lays
+  ground to later linguistic analysis by setting the margins of which parts of
+  the document it has to operate on.
 
-\item[Post processing:] Performs all sorts of content enhancement on the
-annotations of the previous two processing steps.
+\item{ Linguistic processing: }
 
-\end{itemize}
+  All linguistic tasks (tokenization, sentence boundary detection,
+  part-of-speech tagging\ldots{}) on the text-annotations from the previous
+  processing step are performed in this module. This is also the most expensive
+  step from a computational point of view. Optimizations to the code are most
+  likely to yield visible results here.
 
-\subsubsection{HTML Processing}
+\item{ Post processing: }
+
+  Post processing analysis provides annotations on the document text with regard
+  to the enhancement method the user inquired.  \end{itemize}
+
+All steps operate solely on the CAS, UIMA's native document model. This is also
+the most strenous requirement on analysis engines to be integrated into WERTi.
+While external configuration may be read, there should be absolutely no side
+effects outisde the CAS - which is the only stateful entitity during
+linguistic processing.
+
+The next sections will explain all subsequent analysis steps in further detail.
+
+\subsection{HTML Processing}
 
 The HTML processor method was designed to be primitive and efficient. While
-using a fully capable HTML parser was considered, we preffered to use a more
-simple approach since there didn't seem to be any need for the additional data
-an HTML parser could have provided us with. Furthermore, changing the
+using a fully capable HTML parser was considered, we preferred to use a more
+simple approach. Full and formally correct HTML markup was deemed unnecessary and
+too time intensive.
+Furthermore, changing the
 implementation of an analysis step even this fundamental to further processing
@@
 
-\paragraph{Preconditions} We have a document represented as a singleton and
-stored in the UIMA-CAS that is passed to the \verb#process(CAS)#-method of the
+\paragraph{Preconditions} An input document retrieved in during earlier steps
+has been retrieved and it exists in memory as an instance of a singleton
+String\footnote{As usual in UIMA. For large documents, UMIA provides ways of
+splitting up documents and processing the chunks independently. However, UIMA
+only considers documents well beyond one megabyte to be ``big enough'' to be
+split. The plain HTML most web pages serve rarely exceeds this mark.}   and is
+stored in the UIMA CAS. This is then passed to the \verb#process(CAS)#-method of the
 \verb#HTMLAnnotator#-class.
+\paragraph{Postconditions} The document contains annotations marking up the
+positions and spans of html tags in the document text. The names of
+tags\footnote{E.g. ``p'' for the tag \texttt{<p>} or ``<div>'' for the dag
+\texttt{div}.} are
+also stored and a \verb#isClosing#-flag is set, that denotes whether this tag is
+closing another sibling\footnote{A preceding slash in the tag name closes the tag.}.
 
-\subsubsection{Linguistic Processing}
+\subsection{Finding Text to Process}
+
+The next step in the process is to find a way of denoting the text areas that
+will lay the basis for later linguistic processing. Originally this part of the
+analysis engine was far more productive than it is now. It has lost a lot of its
+functionality which has been taken over by the linguistic processing itself.
+
+Currently, its main task is to eliminate whitespace and text between tag pairs
+considered irrelevant, mostly because they contain scripts and meta-information
+not actually rendered to text by the user's client.
+
+This functionality could be further extended by providing hints and special
+caases for certain recommended web sites, such as Wikipedia or various news
+sites. However, since the source layout of most web pages is highly volatile,
+development focus has so far not turned to evaluation of this idea.
+
+\paragraph{Preconditions} The CAS contains full HTML tag annotations.
+\paragraph{Postconditions} The CAS contains a markup of all text that is going
+to be considered by the linguistic processing.
+
+\subsection{Linguistic Processing}
+
+Linguistic processing currently goes through 3 major steps: \emph{Tokenization},
+\emph{Sentence Boundary Detection} and \emph{Part of Speech Tagging}. This
+steps subsequently depend on each other.
+
+\subsubsection{Tokenization}
+
+Tokenization chunks the input from the previous processing steps into tokens of
+natural language. Different tokenizers may perform differently and consider
+different type of input spans to denote ``tokens''. This is especially important
+since later steps may depend on a particular type of tokenization 
+rules\footnote{Part of speech tagging is particularly sensivite to
+tokenization. Penn Tree Bank trained taggers usually require tokenization to
+happen according to the PTB tokenization guidelines. Currently, WERTi's
+tokenizers respect this guidelines, to provide a most general rule processin can
+rely upon}. Several types of Tokenizer have been implemented, with the current
+alternatives being an interface to the Stanford Tagger's
+tokenizer\footnote{Which in turn rips off something else} %% CITATION needed
+and a simple example tokenizer, implemented locally for testing purposes, which
+seems to perform similar in terms of quality, but better in terms of performance
+and is the current default.
+
+\paragraph{Precondition} The CAS contains annotations that denote input data to
+the linguistic processing.
+\paragraph{Postcondition} The CAS contains a set of tokens that can lay the
+ground to all further linguistic analysis.
+
+\subsubsection{Sentence Boundary Detection}
+
+The sentence boundary detector implemented is currently not very advanced and
+simply matches several regular expressions and even single characters considered
+to end a sentence in all cases (\verb#.#, \verb#?# and \verb#!#). This coud be
+improved by making more educated assumptions about the nature of the input
+tokens, but development has not focussed on these issues so far. While part of speech
+tagging does generally benefit from stringent denotations of sentences, the
+tagging process has so far been accurate enough and 
+providing a correct method of sentence boundary detection could prove
+non-trivial to implement. This could also be an entry point for future projects
+to improve the system's functionality, as accurate sentece boundary detection
+is of great importance to syntactic parsing.
+
+\paragraph{Precondition} Annotations in the CAS exist for all relevant input
+tokens in natural language.
+\paragraph{Postcondition} The CAS contains a markup of sentence boundaries. This
+markup only depends on a starting and an ending point within the documnet text,
+possibly spanning tags\footnote{UIMA provides a \texttt{subiterator} method to
+construct an iterator over annotations of a particular type that are subsumed by
+another annotation of arbitrary type. It does not provide a general mechanism
+for implementing distributed annotations that would have multiple beginning and
+ending points.}.
+
+\subsubsection{Part of Speech Tagging}
+
+Part of Speech tagging currently relies solely on external tools. Two taggers
+have so far been implemented: The \emph{Penn Tree Bank Tagger} and the
+\emph{UIMA Sandbox Tagger}. A Java \emph{Interface} in the analysis package
+provides a common abstraction mechanism over the different taggers to be
+implemented. The \verb#Tagger# interface declares processing methods as
+\verb#synchronized#, so calls to the tagging routines are blocking. This ensures
+multiple clients running on the same server will not hinder the tagger in
+processing each call correctly\footnote{No tagger of those evaluated for useage
+provides concurrent processing of input strings since tagging is generally
+deemed to be an expensive step the machine should focus on.}.
+
+Taggers are stored statically in server side context to ensure maximum
+performance as tagger instantiation is typically very costly. Most taggers
+are stateless during tagging, ensuring equal quality of results among calls.
+
+\paragraph{Precondition} The tagging process feeds on two types of annotations:
+\verb'Token's and \verb'Sentence's. It has access to the token annotations via
+calls to the sentence annotation's subiterator.
+
+\paragraph{Postcondition} All \verb'Token' annotations the tagger found tags for
+now carry a ``tag'' field, indicating their part of speech tag.
 
@@
 
-\section{The User Inteface}
+This step depends on
+  annotation results from the two preceeding modules; certain HTML markups are
+  used in order to correctly organize all code later executed on client side.
 
-\subsection{Web Interface}
+\subsection{The User Interface}
 
-\subsection{Programming Interface}
+At the time of writing the user interface to the WERTi platform has not been
+finished yet. As such, this section mostly provides a prespective on desired
+functionality, indicating partial results when they are already implemented.
+
+\subsubsection{The Interactive Web Interface}
+
+WERTi is now a web application, written in the Google Web Toolkit, which
+compiles native AJAX code from Java sources. The toolkit thus provided a
+possibility of increasing the consistnency of the platform's code by ensuring
+that it would be written using only one programming laguage. The user interface
+components rely on RPCs to interact with the server. RPC\footnote{Remote
+Procedure Calls} provides an asynchronous method of interaction between client
+server side code, so the user can be informed about the progress of their
+request and also interact seamlessly with generated enhancements. While basic
+proof of concept for the user interface is already finished, more components
+will be implemented shortly.
+\begin{itemize}
+  \item Users should be provided with an account system and components for
+    evaluating their own progress in certain parts. For this, a basic database
+    interface has been written, connected to the PostgreSQL engine. Calls to the
+    database will be implemented in an asynchronous fashion, making use of
+    non-blocking threading on the server side.
+  \item Input enhancement on the retrieved document should make more use of its
+    potential brought by the underlying framework. The chosen methods would
+    allow for interactive suggestions and on line feedback, as well as the
+    implementation of interesting new features possibly relying on client/server
+    interaction. Partial translation of the document text or only dictionary
+    lookups would be one such method.
+\end{itemize}
+
+The main reason for the user interface to be in a usable, but yet to be finished
+state is that development focus laid on making the back end reliable and stable
+enough to deal with user requests first. With a solid base provided, the user
+interface can now make use of the functionality described earlier in section
+\ref{sec:UIMA}.
 
@@
 
+Writing a system of the complexity of WERTi has proven to be a great and very
+enjoyable challange. Using corporate-grade environments, managing a large and
+constantly growing code base and deploying an interactive web application on web
+servers using very modern technologies have provided the author with great
+insights to the development of larger scale projects. While background in
+computational linguistics was neccessary in order to make the right choices in
+the design of the natural language processing tasks, working on the project also
+required flexibility terms of software engeneering and design, as well as
+knowledge of Internet technology and the principles underlying the World Wide
+Web.
+
+The system itself has grown over the development process, which started on May
+8th, 2008 and is currently continuing. Although it has made significant progress
+and achieved most of its original design goals, the next section will discuss
+some enhancements to the system required in order to bring full usability to
+WERTi.
+
 \subsection{Loose Ends}
 
+WERTi is by now in a mostly usable state. As such the programming project was a
+success, although there still remain some loos ends to be implemented. The
+following enumerates those and discusses possible takes on solving them.
+\begin{itemize}
+\item{Provide Easier Access to Users}
+
+The user interface is largely unwritten and lacks an interface to a web search
+engine such as Google or Yahoo Web Search, in order to retrieve content relevant
+to topics the user specifies.
+
+User accounts and relational databases with user data could be used to track a
+user's success and provide them with positive and negative feedback. E.g.
+showing in which context they regularly fail to give the right preposition or
+determiner, or where they improved their score over time. RPC calls should
+provide sufficient client $\leftrightarrow$ server interaction potential.
+
+\item{Provide a Greater Range of Features}
+
+The analysis engines could also feature lemmatization, shallow parsing,
+(partial) translation and similar mechanisms for providing further methods of
+second language acquisition assistance. %% Yeaaaahah! Found buzzword. Like it.  Aliteration!
+\end{itemize}
+
+Work on the system will continue in an open fashion and additional developers
+are encouraged to provide the author with their own ideas for implementation and
+code contributions to the system. This paper can serve as an entry point to
+understand the system at a more abstract level while the additional
+documentation integrated in the code base should provide developers with easy
+access to the system's inner workings.
 \end{document}

### 2008-06-27 src/org/werti/client/Gonfig.java

@@ -1,2 +1,0 @@
-package org.werti.client;
-

### 2008-06-27 src/org/werti/uima/ae/SimpleTokenizer.java

@@ -40,7 +40,9 @@ public class SimpleTokenizer extends JCasAnnotator_ImplBase {
 			for (int i = 1; i < span.length; i++) {
 				if ((Character.getType(span[i]) != Character.getType(span[i-1]))
 				||   Character.getType(span[i]) == Character.DIRECTIONALITY_WHITESPACE
-				||   span[i] == '.') {
+				||   span[i] == '.'
+				&&  (span[i] == '-' && span[i-1] != Character.DIRECTIONALITY_WHITESPACE)
+				) {
 					final Token t = new Token(cas);
 					t.setBegin(lskew);
 					t.setEnd((lskew = gskew + i));

### 2008-06-27 docs/paper/paper.tex
Finished Paper.

@@
-\documentclass[12pt]{article}
+\documentclass[12pt]{scrartcl}
 
 \usepackage[english]{babel}
+\usepackage{tuebingerspruechle}
 \usepackage{qtree}
@@
 \usepackage[utf8x]{inputenc}
-\usepackage{linguex}
+\usepackage{linguex,natbib,graphicx}
 
 \author{Aleksandar Dimitrov}
-\title{WERTi - Easing Second Language Acquisition}
+\title{Rebuilding WERTi: Providing a Platform
+for Second Language Acquisition Assistance}
+
+\bibliographystyle{plainnat}
 
@@
 
+\SpruechleAufsagen{Aleksandar Dimitrov}
+
 \section{Introduction}
 
-Using tools and methods made available through new achievements in computational
+Using tools and methods made available through recent achievements in computational
 linguistics and related subjects to ease the process of second language
@@
 digitalized versions of traditional data sources like dictionaries have already
-experienced usage to some extent already, we have yet to discover new and
+experienced usage to some extent, we have yet to discover new and
 effective ways of aiding second language acquisition of adult learners. Many
@@
 
-WERTi tries to approach this probmlem from a general perspective. Making
-use of the the momentum of the Internet, WERTi provides a platform for
+WERTi tries to approach this problem from a general perspective. Making
+use of the momentum of the Internet, WERTi provides a platform for
 implementing linguistic analysis and subsequent input enhancement methods on
-user specified pages on the World Wide Web. Using Java Servlet and AJAX technology for
+user specified pages from the World Wide Web. Using Java Servlet and AJAX technology for
 serving content and the UIMA framework for processing it in a dynamic and
-flexible manner, we aim to provide a platform for linguistic processing of
-online content that can go beyond input enhancement.
+flexible manner, the goal is to provide a platform for linguistic processing of
+online content that can go beyond input enhancement and engage new and
+interactive methods.
 
@@
 The original design of WERTi has been developed at Ohio State University by
-\textsc{Detmar Meurers} and his research associates. 
-%% TODO: not only detmar. Who else?
-There exist several papers
-about this original work. 
-%% TODO: Citation Needed
+\textsc{Detmar Meurers}, \textsc{Vanessa Metcalf}, \textsc{Luiz Amaral},
+\textsc{Chris Kovach} and \textsc{Cory Shain}.
+It is accessible at the following internet address:
 
-At Tübingen University the concept has now been extended
-to encompass a wider range of functionality and provide a more scalable
-solution. To achieve this, several enterprise grade technologies have been put to
-use. Although this comes with certain drawbacks (such as an increase in the
-code base by as much as over 1000\%), they provided us with a more flexible and robust
-architecture which should be able to cope with most demands to the system.
+\ex. \texttt{http://prospero.ling.ohio-state.edu/WERTi}
 
-%\subsection{Acknowledgements}
+The underlying research on WERTi is best summarized in \cite{talk1} and \cite{talk2}.
 
-%I'd like to thank my advisor \textsc{Detmar Meurers} for providing me with the
-%unique opportunity on working on the WERTi system. WERTi was originally thought
-%out and developed in Python by him and his team at the Ohio State University. My
-%job was to port the system he had already written to Java using UIMA and
-%generalize the concept as to make it easier to implement new functions.
-
-%I would also like to thank \textsc{Janina Radó}, who provided me with invaluable feedback
-%about the general style guidelines of papers of this kind.
-
-%Furthermore I'd like to thank , , , and for providing testing the system and for
-%their suggestions, remarks and feature requests.
-
+At Tübingen University the concept has now been extended to encompass a wider
+range of functionality and provide a more scalable solution. To achieve this,
+several enterprise grade technologies have been put to use. Although this comes
+with certain drawbacks (such as an increase in the code base by as much as over
+1000\%), they provided the developer with a more flexible and robust architecture which
+should be able to cope with most demands to the system. The development of the
+new system started on May 8th in 2008 and has been going on for one and a half month
+as of writing this paper.\footnote{Acknowledgements:
+I would like to thank my advisor \textsc{Detmar Meurers} for providing
+the unique opportunity on working on the WERTi system. 
+I would also like to thank \textsc{Janina Radó}, who provided invaluable feedback
+about the writing of academic papers and also suggested some features for the
+system.}
+ In this time, a total of over 3300 lines of Java code
+ have been written\footnote{And countless more have been rewritten}, accompanied by about 2000 lines of XML code, mainly in the
+descriptor files for UIMA and the interface models.  Additionally, about 5000
+lines of documentation in HTML have been generated by the system and the
+developer. All of the development progress has been kept track of in a version
+control system, so historical changes are easy to
+comprehend.
 \section{The Development Process}
 
-In this section we will first explain the goals of the reimplementation and then
-display in what environment the project has been written and what technologies
+This section first explains the goals of the reimplementation and then
+displays in what environment the project has been written and what technologies
 have been put to use.
 
-\subsection{Goals of the New Ipmlementation}
+\subsection{Goals of the New Implementation}
 
@@
  written in the programming language
- Python, our new design is rooted in Java
+ Python, the new design is rooted in Java
  technologies and makes use of several frameworks to ensure maximum scalability.
@@
     of the site content in order filter out text for later natural language
-    processing tasks. This way we can provide the user with free choice over the
+    processing tasks. This way the system can provide the user with free choice over the
     target material %% YAY!
-  \item Processing of site content should be generalized and made to be as
+  \item Processing of site content was to  be generalized and made to be as
     flexible as possible in order to ensure maximum extensibility of the
@@
     the results of one of the \emph{Analysis Engines} can always serve as the
-    input to other engines.
-  \item Ensure asynchronous client $\leftrightarrow$ server communication capabilities in
+    input to other engines. Using UIMA, all processing can happen at a
+    meta-level through annotations, while leaving the document text stateless
+    and thus ensuring consistency among processing steps.
+  \item Asynchronous client $\leftrightarrow$ server communication capabilities
+    were to be ensured in
     order to allow evaluation of the user's performance on target texts.
-    Together with an anticipated user account system this would provide us with
+    Together with an anticipated user account system this would provide
     the ability of measuring of a particular user's progress and provide them
     with automated feedback on their abilities.
-  \item Overall we wanted to provide an easy to use, flexible and scalable web 
+  \item Overall the goal was to provide an easy to use, flexible and scalable web 
     based platform for methods of second
@@
 
-\subsection{Design Process} The work on the Java implementation of WERTi happened
-mostly autonomous and was conducted by one person. Given free choice over the
+\subsection{Design Process} The work on the Java implementation of WERTi 
+was mostly conducted by one person. Given free choice over the
 development environment and frameworks, a considerable part of the writing
-process was spent on evaluation and study of the technologies put to use. The
-only notable specifications set on the development environment was the use of
+process was spent on evaluation and study of the technologies to be applied. The
+only notable specifications set on the development environment were the use of
 UIMA, which in turn implied the use of the Java programming language.
@@
 course of the design process, the system was several times restructured and some
-parts of it have by now been rewritten two or even three times.
+parts of it have by now been completely rewritten two or even three times.
 
-Work on the code has been mostly performed using standard UNIX command line
-tools for writing, testing and debugging code, although more advanced solutions
-like the Eclipse Java IDE were also used. They mostly provided easier
-organization of the work within the different frameworks\footnote{Most
-importantly UIMA which comes with a number of useful plugins to easily devise
-analysis engine outlines.}. All of the work has been tracked with a version
+Work on the code has to a great extent been  performed using standard UNIX command line
+tools for writing, testing and debugging code. More advanced solutions
+like the Eclipse Java IDE were also used because of their capabilities which
+allowed for organization of the work within the different frameworks in a more
+straight-forward way\footnote{Most
+importantly UIMA which comes with a number of useful Eclipse plug-ins to easily devise
+analysis engine descriptors.}. All of the work has been tracked with a version
 control\footnote{The author chose to use the \emph{git} version control system,
 which has been and developed for and successfully used in the context of much greater
-codebases, such as the Linux kernel.} system on which further work on the system
+code bases, such as the Linux kernel.} system on which further work on the system
 will also depend.
@@
 All text extraction and natural language processing work is done inside the UIMA
-architecture.  Modifications  to the document's structure are clearly seperated
-from the process of annotating it. In this way we can ensure natural language
-analysis to be a consistent process on one and the same input.
+architecture.  Modifications  to the document's structure are clearly separated
+from the process of annotating it. This allows for ensuring natural language
+analysis is a consistent process on one static input document.
 
@@
 
-\item{ HTML processing: }
+\item{ HTML processing (Pre-Processing): }
 
@@
 
-\item{ Linguistic processing: }
+\item{ Linguistic Processing: }
 
@@
 
-\item{ Post processing: }
+\item{ Enhancement Processing (Post-Processing): }
 
@@
 All steps operate solely on the CAS, UIMA's native document model. This is also
-the most strenous requirement on analysis engines to be integrated into WERTi.
+the most strenuous requirement on analysis engines to be integrated into WERTi.
 While external configuration may be read, there should be absolutely no side
-effects outisde the CAS - which is the only stateful entitity during
+effects outside the CAS - which is the only stateful entity during
 linguistic processing.
@@
 The HTML processor method was designed to be primitive and efficient. While
-using a fully capable HTML parser was considered, we preferred to use a more
-simple approach. Full and formally correct HTML markup was deemed unnecessary and
-too time intensive.
+using a fully capable HTML parser was considered, a more simple approach was
+favored over a fully markup-aware and more heavy parsing.
+Full and formally correct HTML markup was deemed unnecessary and
+parsing too time intensive and error-prone.
 Furthermore, changing the
@@
 split. The plain HTML most web pages serve rarely exceeds this mark.}   and is
-stored in the UIMA CAS. This is then passed to the \verb#process(CAS)#-method of the
-\verb#HTMLAnnotator#-class.
+stored in the UIMA CAS.
 \paragraph{Postconditions} The document contains annotations marking up the
-positions and spans of html tags in the document text. The names of
-tags\footnote{E.g. ``p'' for the tag \texttt{<p>} or ``<div>'' for the dag
-\texttt{div}.} are
-also stored and a \verb#isClosing#-flag is set, that denotes whether this tag is
+positions and spans of HTML tags in the document text. The names of
+tags\footnote{E.g. ``p'' for the tag \texttt{<p>} or ``div'' for the dag
+\texttt{<div>}.} are
+also stored and a flag is set that denotes whether this tag is
 closing another sibling\footnote{A preceding slash in the tag name closes the tag.}.
@@
 
-The next step in the process is to find a way of denoting the text areas that
+The next step in the pipeline is to find a way of denoting the text areas that
 will lay the basis for later linguistic processing. Originally this part of the
-analysis engine was far more productive than it is now. It has lost a lot of its
-functionality which has been taken over by the linguistic processing itself.
+analysis engine was far more productive than it is now. It has lost a large part of its
+functionality which has been taken over by the linguistic processing
+itself.\footnote{Coherence analysis during sentence boundary detection, which is
+explained further on has replaced a more specialized approach of trying to find
+bits of natural language that do not constitute a full text (e.g. choices in a
+menu or short statements in tables.)}
 
@@
 This functionality could be further extended by providing hints and special
-caases for certain recommended web sites, such as Wikipedia or various news
+cases for certain recommended web sites, such as Wikipedia or various news
 sites. However, since the source layout of most web pages is highly volatile,
@@
 natural language. Different tokenizers may perform differently and consider
-different type of input spans to denote ``tokens''. This is especially important
+different type of input spans to denote ``tokens''. Taking this into account is especially important
 since later steps may depend on a particular type of tokenization 
-rules\footnote{Part of speech tagging is particularly sensivite to
+rules\footnote{Part of speech tagging is particularly sensitive to
 tokenization. Penn Tree Bank trained taggers usually require tokenization to
 happen according to the PTB tokenization guidelines. Currently, WERTi's
-tokenizers respect this guidelines, to provide a most general rule processin can
-rely upon}. Several types of Tokenizer have been implemented, with the current
+tokenizers respect this guidelines, to provide a most general rule processing can
+rely on.}. Several tokenizer engines have been implemented, with the current
 alternatives being an interface to the Stanford Tagger's
-tokenizer\footnote{Which in turn rips off something else} %% CITATION needed
+tokenizer\footnote{This tokenizer was written by \textsc{Tim Grow}, \textsc{Teg
+Grenager}, \textsc{Christopher Manning}, \textsc{Jenny Finkel}} 
 and a simple example tokenizer, implemented locally for testing purposes, which
@@
 
-\paragraph{Precondition} The CAS contains annotations that denote input data to
-the linguistic processing.
-\paragraph{Postcondition} The CAS contains a set of tokens that can lay the
+\paragraph{Precondition} The CAS contains annotations that denote possible input to
+linguistic processing tasks.
+\paragraph{Postcondition} The CAS contains a set of token annotations that can lay 
 ground to all further linguistic analysis.
@@
 simply matches several regular expressions and even single characters considered
-to end a sentence in all cases (\verb#.#, \verb#?# and \verb#!#). This coud be
+to end a sentence in all cases (\verb#.#, \verb#?# and \verb#!#). This could be
 improved by making more educated assumptions about the nature of the input
@@
 non-trivial to implement. This could also be an entry point for future projects
-to improve the system's functionality, as accurate sentece boundary detection
+to improve the system's functionality, as accurate sentence boundary detection
 is of great importance to syntactic parsing.
+
+This step also analyzes the denoted sentence's \emph{coherence}. This means, it
+takes a simple statistical measure into account that compares the volume of text
+against the number and length of tags over the sentence's span in the raw
+document text. This has proven to be useful in avoiding ``enhancement'' of user
+interfaces of web pages and other elements not desirable as targets for input
+enhancement.
 
@@
 \paragraph{Postcondition} The CAS contains a markup of sentence boundaries. This
-markup only depends on a starting and an ending point within the documnet text,
-possibly spanning tags\footnote{UIMA provides a \texttt{subiterator} method to
+markup only depends on a starting and an ending point within the document text,
+possibly spanning HTML tags\footnote{UIMA provides a \texttt{subiterator} method to
 construct an iterator over annotations of a particular type that are subsumed by
@@
 for implementing distributed annotations that would have multiple beginning and
-ending points.}.
+ending points.}. The sentence annotations also contain coherence values between
+0 and 1, with 1 denoting maximum coherence (only text tokens and no tags) and 0
+denoting minimum coherence.
 
@@
 Part of Speech tagging currently relies solely on external tools. Two taggers
-have so far been implemented: The \emph{Penn Tree Bank Tagger} and the
+have so far been implemented: The \emph{Penn Tree Bank Tagger}\footnote{Written
+by \textsc{Kristina Toutanova}, \textsc{Miler Lee}, \textsc{Joseph Smarr},
+\textsc{Anna Rafferty}} and the
 \emph{UIMA Sandbox Tagger}. A Java \emph{Interface} in the analysis package
@@
 multiple clients running on the same server will not hinder the tagger in
-processing each call correctly\footnote{No tagger of those evaluated for useage
+processing each call correctly\footnote{No tagger of those evaluated for usage
 provides concurrent processing of input strings since tagging is generally
-deemed to be an expensive step the machine should focus on.}.
+deemed to be an expensive step the machine performing it should focus on.}.
 
@@
 
-\paragraph{Precondition} The tagging process feeds on two types of annotations:
+Taking into account sentence coherence a explained earlier is not enforced, but
+encouraged.
+
+\paragraph{Precondition} The CAS contains annotations denoting tokens of natural
+language and sentences thereof. The tagging process feeds on two types of annotations:
 \verb'Token's and \verb'Sentence's. It has access to the token annotations via
@@
 \paragraph{Postcondition} All \verb'Token' annotations the tagger found tags for
-now carry a ``tag'' field, indicating their part of speech tag.
+now carry a ``tag'' field, indicating their part of speech tag. The annotator
+engine does not create new tag annotations, but retains a semantic relationship
+between tokens and their part of speech tags by using an annotation field to
+store the tag in.
 
@@
 This step depends on
-  annotation results from the two preceeding modules; certain HTML markups are
+  annotation results from the two preceding modules; certain HTML markups are
   used in order to correctly organize all code later executed on client side.
+  While this is the last step performed by the analysis engines, it is still
+  non-destructive with respect to the document text as it only marks entry
+  points for enhancement code. Every annotation contains a list of document
+  positions and a corresponding list of enhancement strings to be put into the
+  respective document positions. Each enhancement also covers a certain span -
+  this way the enhancement process which generates the final HTML page to be
+  returned to the user can make sure enhancements don't overlap or conflict.
+
+  \paragraph{Precondition} There exist annotations in the CAS which can be used
+  as anchor points for enhancements. Different post processing modules will
+  depend on different kinds of annotations. The current \verb#PoSEnhancer#
+  depends on \verb#Token# annotations which carry information about their
+  part of speech tags.
+  \paragraph{Postcondition} The CAS contains enhancement annotations the main
+  system can use to enhance the document.
 
@@
 At the time of writing the user interface to the WERTi platform has not been
-finished yet. As such, this section mostly provides a prespective on desired
+finished yet. As such, this section mostly provides a perspective on desired
 functionality, indicating partial results when they are already implemented.
@@
 compiles native AJAX code from Java sources. The toolkit thus provided a
-possibility of increasing the consistnency of the platform's code by ensuring
-that it would be written using only one programming laguage. The user interface
-components rely on RPCs to interact with the server. RPC\footnote{Remote
-Procedure Calls} provides an asynchronous method of interaction between client
+possibility of increasing the consistency of the platform's code by ensuring
+that it would be written using only one programming language. The user interface
+components rely on RPCs to interact with the server. RPCs\footnote{Remote
+Procedure Calls} provide an asynchronous method of interaction between client
 server side code, so the user can be informed about the progress of their
@@
 proof of concept for the user interface is already finished, more components
-will be implemented shortly.
+will be implemented shortly. Some of the functionality intended for the system
+includes:
 \begin{itemize}
@@
     interaction. Partial translation of the document text or only dictionary
-    lookups would be one such method.
+    lookups would be one such feature.
 \end{itemize}
@@
 
+\subsection{Summary: A General Overview}
+
+A bird's eye view of the system's architecture is provided in \ref{digraph}.
+
+\begin{figure}[htp]\label{digraph}
+  \centering
+  \includegraphics[scale=0.45,angle=90]{architecture}
+  \caption{A simple overview of WERTi's current architecture}
+\end{figure}
+
+Here the arrows denote general a communication pipeline between two components. The
+graph shows how the system is divided into a client side (using AJAX written
+with the GWT), a server side (the Tomcat server) and a UIMA component on server
+side. Requests from the client side are interpreted by the RPC server and yield
+an HTTP request to a certain web site. This site's content is then passed on the
+UIMA CAS, which in turn feeds the analysis steps. The RPC server is also
+responsible for providing a per-user configuration object the server side uses
+to represent the users demands. Any component can read data from the
+configuration on server side, thus the relations to it are not shown. Linguistic processing, as
+shown here also depends on external tools to accomplish its task. The annotators
+feed the CAS with annotations, but their interdependence is not displayed in the
+graph, to maintain simplicity. A server-side enhancement engine then uses the
+Annotations and the CAS to create the document to be returned to the user.
+
 \section{Conclusion}
@@
 Writing a system of the complexity of WERTi has proven to be a great and very
-enjoyable challange. Using corporate-grade environments, managing a large and
+enjoyable challenge. Using corporate-grade environments, managing a large and
 constantly growing code base and deploying an interactive web application on web
@@
 insights to the development of larger scale projects. While background in
-computational linguistics was neccessary in order to make the right choices in
+computational linguistics was necessary in order to make the right choices in
 the design of the natural language processing tasks, working on the project also
-required flexibility terms of software engeneering and design, as well as
+required flexibility in terms of software engineering and design, as well as
 knowledge of Internet technology and the principles underlying the World Wide
@@
 
-The system itself has grown over the development process, which started on May
-8th, 2008 and is currently continuing. Although it has made significant progress
-and achieved most of its original design goals, the next section will discuss
+The system itself has grown over the development process, 
+which is currently continuing. Although it has made significant progress
+and achieved most of its original design goals, the final section will also discuss
 some enhancements to the system required in order to bring full usability to
@@
 WERTi is by now in a mostly usable state. As such the programming project was a
-success, although there still remain some loos ends to be implemented. The
-following enumerates those and discusses possible takes on solving them.
-\begin{itemize}
+success, although there still remain some loose ends to be implemented. \begin{itemize}
 \item{Provide Easier Access to Users}
@@
 User accounts and relational databases with user data could be used to track a
-user's success and provide them with positive and negative feedback. E.g.
+particular user's success and provide them with positive and negative feedback, e.g.
 showing in which context they regularly fail to give the right preposition or
 determiner, or where they improved their score over time. RPC calls should
-provide sufficient client $\leftrightarrow$ server interaction potential.
+provide sufficient client $\leftrightarrow$ server interaction capabilities for
+this.
 
@@
 access to the system's inner workings.
+
+\bibliography{bib}
+
 \end{document}

### 2008-07-01 web/org.werti.Enhancements/org.werti.Enhancements.nocache.js
Meh.

@@ -1,0 +1,11 @@
+function org_werti_Enhancements(){var l='',B='" for "gwt:onLoadErrorFn"',z='" for "gwt:onPropertyErrorFn"',Ab='"><\/script>',n='/',kb='554FA1957D8CA44CB270E3FA5CD81A79.cache.html',zb='<script id="',wb="<script>org_werti_Enhancements.onInjectionDone('org.werti.Enhancements')<\/script>",v='=',jb='AAD58EA97F2A158608157BADE6401B29.cache.html',ib='B74223BC92A149A9B6B82BF77E29B9F0.cache.html',y='Bad handler "',sb='DOMContentLoaded',Bb='SCRIPT',yb='__gwt_marker_org.werti.Enhancements',o='base',q='clear.cache.gif',u='content',db='gecko',eb='gecko1_8',nb='gwt.hybrid',lb='gwt/standard/standard.css',A='gwt:onLoadErrorFn',w='gwt:onPropertyErrorFn',t='gwt:property',rb='head',hb='hosted.html?org_werti_Enhancements',qb='href',bb='ie6',tb='iframe',p='img',ub="javascript:''",mb='link',r='meta',gb='moduleRequested',ab='msie',s='name',D='opera',m='org.werti.Enhancements',vb='position:absolute;width:0;height:0;border:none',ob='rel',F='safari',xb='selectionDone',cb='selectionStart',x='startup',pb='stylesheet',fb='unknown',C='user.agent',E='webkit';var Db=window,k=document,fc=Db.external,Cb=Db.__gwtstatsEvent?function(a,b,c,d){Db.__gwtstatsEvent(a,b,c,d)}:null,sc,ic,cc,bc=l,lc={},vc=[],rc=[],ac=[],oc,qc;Cb&&Cb(m,x,cb,{millis:(new Date()).getTime()});if(!Db.__gwt_stylesLoaded){Db.__gwt_stylesLoaded={}}if(!Db.__gwt_scriptsLoaded){Db.__gwt_scriptsLoaded={}}function hc(){try{return fc&&(fc.gwtOnLoad&&Db.location.search.indexOf(nb)==-1)}catch(a){return false}}
[…]

### 2008-07-01 web/org.werti.WERTi/org.werti.WERTi.nocache.js

@@ -1,11 +1,11 @@
-function org_werti_WERTi(){var l='',B='" for "gwt:onLoadErrorFn"',z='" for "gwt:onPropertyErrorFn"',Db='"><\/script>',n='/',ib='39FE9C074DB289A2327A3107714FACC1.cache.html',kb='502ED2B06E5060F8492AF7F3BCA53279.cache.html',mb='633215CA50C4A7023CEB43AD3F002F02.cache.html',jb='6BD6ADB94AA47D3183467BAD7B65CB6F.cache.html',Cb='<script id="',Ab="<script>org_werti_WERTi.onInjectionDone('org.werti.WERTi')<\/script>",v='=',y='Bad handler "',lb='D195A71DA430545575CEA9E62A25B8C9.cache.html',vb='DOMContentLoaded',Eb='SCRIPT',ub='WERTi.css',Bb='__gwt_marker_org.werti.WERTi',o='base',q='clear.cache.gif',u='content',db='gecko',eb='gecko1_8',nb='gwt.hybrid',ob='gwt/standard/standard.css',A='gwt:onLoadErrorFn',w='gwt:onPropertyErrorFn',t='gwt:property',tb='head',hb='hosted.html?org_werti_WERTi',sb='href',bb='ie6',wb='iframe',p='img',xb="javascript:''",pb='link',r='meta',gb='moduleRequested',ab='msie',s='name',D='opera',m='org.werti.WERTi',zb='position:absolute;width:0;height:0;border:none',qb='rel',F='safari',yb='selectionDone',cb='selectionStart',x='startup',rb='stylesheet',fb='unknown',C='user.agent',E='webkit';var ac=window,k=document,ic=ac.external,Fb=ac.__gwtstatsEvent?function(a,b,c,d){ac.__gwtstatsEvent(a,b,c,d)}:null,vc,lc,fc,ec=l,oc={},yc=[],uc=[],dc=[],rc,tc;Fb&&Fb(m,x,cb,{millis:(new Date()).getTime()});if(!ac.__gwt_stylesLoaded){ac.__gwt_stylesLoaded={}}if(!ac.__gwt_scriptsLoaded){ac.__gwt_scriptsLoaded={}}function kc(){try{return ic&&(ic.gwtOnLoad&&ac.location.search.indexOf(nb)==-1)}catch(a){return false}}
[…]

### 2008-07-03 docs/paper/paper.tex
Temporary commit

--- 2008-06-26 docs/paper/paper.tex
@@
 \usepackage{qtree}
-\usepackage{aleks}
 \usepackage[utf8x]{inputenc}
@@
 
-This section will explain the principles underlying WERTi's functionality by
-first looking at the data processing architecture and then showing how this is
-then integrated into the user interface of the web application.
-
 \subsection{UIMA Analysis Engines}
@@
 The current processing line can be split up into three different parts that can
-interact autonomously but each depend on the output of their predecessor. The
-components are arranged in the following order:
+interact autonomously themselves but each depend on the output of their
+predecessor. The components are arranged in the following manner:
 
@@
 \item[HTML processing:] annotates HTML tags, finds ``relevant'' text within the
-tags. This lays ground to later linguistic analysis by setting the margins of
-where the latter has to operate on in the web content.
+tags.
 
 \item[Linguistic processing:] performs linguistic tasks (tokenization, sentence
-boundary detection, part-of-speech tagging\ldots{}) on the text-annotations
-from the previous processing step. This is also the most intensive step from a
-computational point of view. Optimizations to the code are most likely to yield
-visible results here.
+boundary detection, part-of-speech tagging\ldots{}) on the text-annoatations
+from the previous processing step.
 
 \item[Post processing:] Performs all sorts of content enhancement on the
-annotations of the previous two processing steps. Note that this step depends on
-both annotation results: it also needs certain HTML markups in order to
-correctly organize all of the code that is going to be executed on client side.
+annotations of the previous two processing steps.
 
@@
 
-We will now go on and explain those steps in further detail.
-
 \subsubsection{HTML Processing}
-
-The HTML processor method was designed to be primitive and efficient. While
-using a fully capable HTML parser was considered, we preferred to use a more
-simple approach. Full and formally correct HTML markup was deemed unnecessary and
-too time intensive.
-Furthermore, changing the
-implementation of an analysis step even this fundamental to further processing
-should be easy and without side-effects as long as the requirements to
-preconditions and postconditions are met.
-
-\paragraph{Preconditions} We have a document represented as a singleton
-String\footnote{As usual in UIMA. For large documents, UMIA provides ways of
-splitting up documents and processing the chunks independently. However, UIMA
-only considers documents well beyond one megabyte to be ``big enough'' to be
-split and the plain HTML most web pages serve rarely exceeds this mark.}   and
-stored in the UIMA-CAS that is passed to the \verb#process(CAS)#-method of the
-\verb#HTMLAnnotator#-class.
-\paragraph{Postconditions} The document contains annotations marking up the
-positions and spans of html tags in the document text. The names of
-tags\footnote{E.g. ``p'' for the tag \texttt{<p>} or ``div'' for the dag
-\texttt{div}.} are
-also stored and a \verb#isClosing#-flag is set, that denotes whether this tag is
-closing another\footnote{A preceding slash in the tag name closes the tag.}.
 
@@
 
-Linguistic processing goes through 3 major steps: \emph{Tokenization},
-\emph{Sentence Boundary Detection}
-
 \subsubsection{Post Processing - Input Enhancement}
 
-\section{The User Interface}
+\section{The User Inteface}
 
@@
 \subsection{Programming Interface}
-
-\section{The Development Process}
-In this section I want to display in what environment the project has been
-written and what technologies have been put to use.
-
-\subsection{Concept \& Design}
-The original design of WERTi has been developed at Ohio State University by
-\textsc{Detmar Meurers} and his research associates. There exist several papers
-about this original work. At Tübingen University the concept has been extended
-to
-
-\subsection{Design Process} My Work on the Java implementation of WERTi was
-mostly autonomous. I had been given free choice over the frameworks and
-development environment I wanted to put to use, with the only exceptions being
-being using \emph{Java} and the UIMA architecture to achieve maximum flexibility
-and portability. Maximum flexibility and extensibility were the main goals of
-the re-implementation.
-
-Development happened in a very productive atmosphere with weekly project
-meetings where core functionality and the design of the analysis process were
-discussed. After those most important aspects of the system were implemented, I
-continued work on the interface and extension of the analysis process mostly
-alone for organizational reasons.
-
-I chose to use mostly standard UNIX command line tools for writing, testing and
-debugging the code, although more advanced solutions like the Eclipse Java IDE
-were also used - mostly for easier organization of the work with the different
-frameworks\footnote{Especially UIMA which comes with a number
 

### 2008-07-03 src/org/werti/Interface.java

@@ -1,11 +1,6 @@
 package org.werti;
 
 import java.io.*;
-import java.io.BufferedReader;
-
-import java.net.MalformedURLException;
-import java.net.URL;
-import java.net.URLConnection;
 
 import java.util.Iterator;
 import java.util.Map;
@@ -16,6 +11,8 @@ import java.util.logging.Level;
 import javax.servlet.*;
 
 import javax.servlet.http.*;
+
+import lib.html.Net;
 
 import org.apache.uima.UIMAFramework;
 
@@ -36,17 +33,14 @@ import org.apache.uima.util.XMLInputSource;
 import org.werti.uima.types.Enhancement;
 
 /**
- * This will, according to its arguments, call the appropriate classes that
+ * It will, according to its arguments, call the appropriate classes that
  * are needed to fulfill a specific task.
  */
 
 public class Interface extends HttpServlet {
 	static final long serialVersionUID = 0;
-	private static final String PREFIX = "/var/local/resources/werti/descriptors/";
-	private static final String ENHNCE = PREFIX + "enhancers/PoSEnhancer.xml";
-
-	// maximum amount of of ms to wait for a web-page to load
-	private static final int MAX_WAIT = 1000 * 10;
+	private static final String PREFIX = "/var/local/werti/resources/descriptors/";
+	private static final String ENHNCE = "/home/aleks/src/werti/desc/enhancers/PoSEnhancer.xml";
 
 	private static final Logger log = Logger.getLogger("org.werti");
 
@@ -63,6 +57,9 @@ public class Interface extends HttpServlet {
 		final String tokenizer = request.getParameter("tokenizer");
 		final String enhance = request.getParameter("enhance");
 
+		final String baseurl = Net.find_baseurl(termOrURL);
+		log.fine("Fetching: " + termOrURL + "; baseurl = " + baseurl);
+
 		// log this event's arguments
 		final Map<String,String[]> args = request.getParameterMap();
 		for (final Map.Entry<String,String[]> e: args.entrySet()) {
@@ -74,53 +71,40 @@ public class Interface extends HttpServlet {
 			log.config(e.getKey() + " = " + r);
 		}
 
-		final String descriptor = PREFIX + "operators/" + tokenizer + "-" + tagger + "-hil.xml";
+		final String descriptor = PREFIX + tokenizer + "-" + tagger + "-hil.xml";
 		log.config("Calling descriptor " + descriptor);
 
[…]

### 2008-07-03 src/org/werti/RequestReuters.java

@@ -1,0 +1,98 @@
+package org.werti;
+
+import java.io.*;
+
+import java.net.MalformedURLException;
+
+import java.util.Enumeration;
+
+import java.util.logging.*;
+
+import javax.servlet.*;
+
+import javax.servlet.http.*;
+
+import lib.html.Net;
+
+public class RequestReuters extends HttpServlet {
+	static final long serialVersionUID = 0;
+	private static final Logger log = Logger.getLogger("org.werti");
+
+	/**
+	 * Fetch the article, replace some html-elements so the site doesn't display completely
+	 * awkward and print it to the screen.
+	 *
+	 * This could probably be done cleaner with DOM, but using regexps is arguably more 
+	 * efficient.
+	 *
+	 * The Regexps must be refined to not overgenerate. Currently the last two are especially
+	 * dangerous. They're going to match a whole lot of stuff that might not be their job.
+	 * For example, in the middle of a path something like var='value'/somewhere (although this
+	 * is unlikely.
+	 *
+	 * This method is still very flaky and should probably be refactored to exist in a UIMAn
+	 * context.
+	 */
+	public void doGet(HttpServletRequest request, HttpServletResponse response)
+		throws IOException, ServletException {
+		log.setLevel(Level.FINEST);
+
+		final String article = request.getParameter("url");
+		final String baseurl = Net.find_baseurl(article);
+		final PrintWriter out = response.getWriter();
+		final BufferedReader in = Net.fetch(article);
+
+		response.setContentType("text/html");
+
+		log.info("Fetched " + article);
+		log.info("baseurl: " + baseurl);
+
+		if (!in.ready()) {
+			log.severe("Input stream to " + article + " not ready!");
+		}
+
+		try {
+			//String b = "";
+			while (in.ready()) {
+				final String line = in.readLine();
+				out.print( (line
+				      + "\n"
+				      // FIXME doesn't account for relative paths
+					).replaceAll("href=\"/", "href=\"" + baseurl
+					).replaceAll("background=\"", "background=\"" + baseurl
+					).replaceAll("src=\"/", "src=\"" + baseurl
+					).replaceAll("@import\\s*\"/", "@import \"" + baseurl
+					//).replaceAll("\"/", "\"" + baseurl // FIXME: this is dirty...
+					//).replaceAll("'/", "'" + baseurl // FIXME: this is dirty...
+					));
+			}
[…]

### 2008-07-03 src/org/werti/RequestURL.java

@@ -1,0 +1,55 @@
+package org.werti;
+
+import java.io.*;
+
+import java.util.logging.*;
+
+import javax.servlet.*;
+
+import javax.servlet.http.*;
+
+import lib.html.ErrorPage;
+import lib.html.Net;
+
+import org.werti.uima.Config;
+import org.werti.uima.Dispatcher;
+
+public class RequestURL extends HttpServlet {
+	static final long serialVersionUID = 0;
+	private static final Logger log = Logger.getLogger("org.werti");
+
+	/**
+	 * Fetch the article.
+	 */
+	public void doGet(HttpServletRequest request, HttpServletResponse response)
+		throws IOException, ServletException {
+		final String article = request.getParameter("url");
+		final String baseurl = Net.find_baseurl(article);
+		final PrintWriter out = response.getWriter();
+		final BufferedReader in = Net.fetch(article);
+
+		response.setContentType("text/html");
+
+		log.info("Fetched " + article);
+		log.info("baseurl: " + baseurl);
+
+		if (!in.ready()) {
+			log.severe("Input stream to " + article + " not ready!");
+		}
+
+		try {
+			final Dispatcher d = new Dispatcher(new Config(
+						"/home/aleks/src/werti/desc/testers/PTBTest.xml", baseurl), out);
+			d.process(in);
+			out.print(d.get_results());
+		} catch (org.werti.uima.UnrecoverableUIMAException uuimae) {
+			ErrorPage.show(out, uuimae);
+		}
+	}
+
+	public void doPost(HttpServletRequest request, HttpServletResponse response)
+		throws IOException, ServletException {
+		log.info("Fetching " + request.getParameter("url"));
+		doGet(request, response);
+	}
+}

### 2008-07-03 src/org/werti/RequestWiki.java

@@ -1,0 +1,75 @@
+package org.werti;
+
+import java.io.*;
+
+import java.net.MalformedURLException;
+
+import java.util.Enumeration;
+
+import java.util.logging.*;
+
+import javax.servlet.*;
+
+import javax.servlet.http.*;
+
+import lib.html.Net;
+
+public class RequestWiki extends HttpServlet {
+	static final long serialVersionUID = 0;
+	private static final Logger log = Logger.getLogger("org.werti");
+
+	public void doGet(HttpServletRequest request, HttpServletResponse response)
+		throws IOException, ServletException {
+		log.setLevel(Level.FINEST);
+		response.setHeader("host", "en.wikipedia.org");
+		response.setContentType("text/html");
+		PrintWriter out = response.getWriter();
+		final String article = request.getParameter("wikiquery");
+		log.info("Fetched " + article);
+		try {
+			logResponseHeader(response);
+			logRequestHeader(request);
+			String b = "";
+			final BufferedReader in = Net.fetch(wikify(article));
+			while (in.ready()) {
+				b += (in.readLine() + "\n"
+						).replaceAll("href=\"/", "href=\"" + "http://en.wikipedia.org/"
+						).replaceAll("src=\"/", "src=\"" + "http://en.wikipedia.org/"
+						).replaceAll("@import\\s*\"/", "@import \"" + "http://en.wikipedia.org/"
+						).replaceAll("\"/", "\"" + "http://en.wikipedia.org/")
+						;
+			}
+			out.print(b);
+		} catch (MalformedURLException mue) {
+			log.log(Level.SEVERE, "Malformed URL", mue);
+		} catch (IOException ioe) {
+			log.log(Level.SEVERE, "Wrong content?", ioe);
+		}
+	}
+
+	private static void logRequestHeader(HttpServletRequest r) {
+		log.fine("ContextPath: " + r.getContextPath());
+		final Enumeration<String> e = r.getHeaderNames();
+		while (e.hasMoreElements()) {
+			final String s = e.nextElement();
+			log.fine("Header: " + s + "\n" + r.getHeader(s));
+		}
+
+
+	}
+
+	private static void logResponseHeader(HttpServletResponse r) {
+
+	}
+
+	private static String wikify(String term) {
+		return "http://en.wikipedia.org/wiki/" + term.replace(" ", "_");
+	}
+
+	public void doPost(HttpServletRequest request, HttpServletResponse response)
[…]

### 2008-07-03 src/org/werti/client/WERTi.java

@@ -1,13 +1,11 @@
 package org.werti.client;
 
-
 import com.google.gwt.core.client.EntryPoint;
+import com.google.gwt.core.client.GWT;
 
 import com.google.gwt.dom.client.Document;
 import com.google.gwt.dom.client.HeadElement;
 import com.google.gwt.dom.client.LinkElement;
-
-
 
 import com.google.gwt.user.client.ui.Button;
 import com.google.gwt.user.client.ui.ClickListener;
@@ -16,10 +14,12 @@ import com.google.gwt.user.client.ui.DialogBox;
 import com.google.gwt.user.client.ui.HTML;
 import com.google.gwt.user.client.ui.Label;
 import com.google.gwt.user.client.ui.RootPanel;
-import com.google.gwt.user.client.ui.SimplePanel;
 import com.google.gwt.user.client.ui.VerticalPanel;
 import com.google.gwt.user.client.ui.Widget;
 
+/**
+ * Entry point classes define <code>onModuleLoad()</code>.
+ */
 public class WERTi implements EntryPoint {
 
 	private Label styleTester;
@@ -47,18 +47,38 @@ public class WERTi implements EntryPoint {
 		RootPanel.get().add(styleTester);
 
 		// Create the constants
-		// WERTiConstants constants = (WERTiConstants) GWT.create(WERTiConstants.class);
+		WERTiConstants constants = (WERTiConstants) GWT.create(WERTiConstants.class);
 
 		// Create the User Interface
-		app = new Application();
+		app = new WERTiUI();
 
-                /*
-		 *setupTitlePanel(constants);
-		 *setupMainLinks(constants);
-		 *setupOptionsPanel();
-		 *setupMainMenu(constants);
-                 */
+		setupTitlePanel(constants);
+		setupMainLinks(constants);
+		setupOptionsPanel();
+		setupMainMenu(constants);
 		RootPanel.get().add(app);
+
+
+		// Create the dialog box
+		final DialogBox dialogBox = new DialogBox();
+		dialogBox.setText("Welcome to GWT!");
+		dialogBox.setAnimationEnabled(true);
+		Button closeButton = new Button("close");
+		VerticalPanel dialogVPanel = new VerticalPanel();
+		dialogVPanel.setWidth("100%");
+		dialogVPanel.setHorizontalAlignment(VerticalPanel.ALIGN_CENTER);
+		dialogVPanel.add(closeButton);
+
[…]

### 2008-07-03 src/org/werti/uima/Config.java

@@ -1,0 +1,25 @@
+package org.werti.uima;
+
+public class Config {
+	private final String desc;
+	private final String baseurl;
+
+	public Config() {
+		desc = "Bogus";
+		baseurl = "bogus";
+
+	}
+
+	public Config(String desc, String baseurl) {
+		this.desc = desc;
+		this.baseurl = baseurl;
+	}
+
+	public String getDescriptor() {
+		return desc;
+	}
+
+	public String getBaseURL() {
+		return baseurl;
+	}
+}

### 2008-07-03 src/org/werti/uima/Dispatcher.java

@@ -1,0 +1,217 @@
+package org.werti.uima;
+
+import java.io.BufferedReader;
+import java.io.IOException;
+import java.io.InputStream;
+import java.io.InputStreamReader;
+import java.io.PrintWriter;
+
+import java.util.Iterator;
+
+import java.util.logging.*;
+
+import org.apache.uima.UIMAFramework;
+
+import org.apache.uima.analysis_engine.AnalysisEngine;
+import org.apache.uima.analysis_engine.AnalysisEngineProcessException;
+
+import org.apache.uima.cas.FSIndex;
+
+import org.apache.uima.jcas.JCas;
+
+import org.apache.uima.jcas.cas.IntegerArray;
+import org.apache.uima.jcas.cas.StringArray;
+
+import org.apache.uima.resource.ResourceInitializationException;
+import org.apache.uima.resource.ResourceSpecifier;
+
+import org.apache.uima.util.InvalidXMLException;
+import org.apache.uima.util.XMLInputSource;
+
+import org.werti.uima.types.Enhancement;
+
+public class Dispatcher {
+
+	private final JCas cas;
+	private final AnalysisEngine ae;
+	private final PrintWriter out;
+	private final String baseurl;
+
+	private static final Logger log = Logger.getLogger("org.werti");
+
+	/**
+	 * Initialize the Dispatcher with a given config.
+	 *
+	 * We initialize the dispatcher's fields, namely we construct the given analysis 
+	 * engine and the CAS.
+	 *
+	 * This can be a source of breakdown. If we can't initialize because we can't read
+	 * or find the XML descriptor, of it its XML is corrupt, we have to abort 
+	 * ungracefully. I know no other way around it. Inserting a default value in 
+	 * this case is bound to cause all sorts of trouble, especially if the error is
+	 * system wide (all descriptors unreadable, etc...)
+	 *
+	 * We therefore throw an UrecoverableUIMAException to inform the caller that
+	 * they should go fix teir code. Be careful what you throw at this thing.
+	 */
+	public Dispatcher(Config cfg, PrintWriter out) throws UnrecoverableUIMAException {
+		try {
+			final XMLInputSource in = new XMLInputSource(cfg.getDescriptor());
+			baseurl = cfg.getBaseURL();
+			final ResourceSpecifier spec = 
+				UIMAFramework
+				.getXMLParser()
+				.parseResourceSpecifier(in);
+				
[…]

### 2008-07-03 src/org/werti/uima/ae/HMMTagger.java

@@ -2,6 +2,7 @@ package org.werti.uima.ae;
 
 import java.io.FileInputStream;
 import java.io.IOException;
+import java.io.InputStream;
 import java.io.ObjectInputStream;
 
 import java.util.ArrayList;
@@ -39,11 +40,11 @@ public class HMMTagger extends JCasAnnotator_ImplBase implements Tagger {
 	 */
 	// n-gram model
 	private static final String pN = "NGRAM_SIZE";
-	private static int N;
+	private int N;
 
 	// model generation
 	private static final String pModel = "MODEL_LOCATION";
-	private static ModelGeneration model;
+	private ModelGeneration model;
 
 	/**
 	 * Initializes the HMMTagger with a model supplied by the configuration-resource
@@ -54,10 +55,8 @@ public class HMMTagger extends JCasAnnotator_ImplBase implements Tagger {
 	public void initialize(final UimaContext context) throws ResourceInitializationException {
 		super.initialize(context);
 		try {
-			N = (Integer) context.getConfigParameterValue(pN);
-			if (model == null) {
-				model = get_model(context);
-			}
+			this.N = (Integer) context.getConfigParameterValue(pN);
+			this.model = get_model(context);
 		} catch (AnnotatorConfigurationException ace) {
 			throw new ResourceInitializationException(ace);
 		} catch (Exception e) {
@@ -74,15 +73,16 @@ public class HMMTagger extends JCasAnnotator_ImplBase implements Tagger {
 	// initialize the model
 	private static ModelGeneration get_model(final UimaContext context, final String loc)
 		throws AnnotatorConfigurationException {
-		final ObjectInputStream ois;
+		final InputStream model;
 		try {
 			if (loc == null || loc.equals("")) {
 				// fetch model from Annotator configuration
 				final String resource = (String) context.getConfigParameterValue(pModel);
-				ois = new ObjectInputStream(new FileInputStream(resource));
+				model = ClassLoader.getSystemResourceAsStream(resource);
 			} else {
-				ois = new ObjectInputStream(new FileInputStream(loc));
+				model = new FileInputStream(loc);
 			}
+			final ObjectInputStream ois = new ObjectInputStream(model);
 			final ModelGeneration oRead = (ModelGeneration) ois.readObject();
 			return oRead;
 		} catch (IOException ioe) {
[…]

### 2008-07-03 src/org/werti/uima/ae/HTMLAnnotator.java

@@ -4,8 +4,6 @@ package org.werti.uima.ae;
 
 import org.apache.uima.analysis_component.JCasAnnotator_ImplBase;
 
-import org.apache.uima.cas.FSIndex;
-
 import org.apache.uima.jcas.JCas;
 
 import org.apache.uima.util.Level;
@@ -31,7 +29,6 @@ public class HTMLAnnotator extends JCasAnnotator_ImplBase {
 		getContext().getLogger().log(Level.INFO,
 				"Starting HTML tag recognition");
 		final String s = cas.getDocumentText();
-		getContext().getLogger().log(Level.FINEST, "DocumentText is " + s.length() + " characters long");
 		int tstart = 0;
 		int tend = 0;
 		while ((tstart = s.indexOf('<', tstart)) > -1) {
@@ -65,9 +62,8 @@ public class HTMLAnnotator extends JCasAnnotator_ImplBase {
 			tag.addToIndexes();
 
 		}
-		final FSIndex fsi = cas.getAnnotationIndex(HTML.type);
 		getContext().getLogger().log(Level.INFO,
-				"Finished HTML tag recognition. Recognized " + fsi.size() + " tags.");
+				"Finished HTML tag recognition");
 	}
 
 	// skips ahead and marks irrelevant tags

### 2008-07-03 src/org/werti/uima/ae/LingPipeTagger.java

@@ -1,66 +1,20 @@
 package org.werti.uima.ae;
 
-import java.util.Iterator;
-
-import com.aliasi.corpus.TagHandler;
-
 import org.apache.uima.UimaContext;
 
 import org.apache.uima.analysis_component.JCasAnnotator_ImplBase;
-
-import org.apache.uima.cas.text.AnnotationIndex;
 
 import org.apache.uima.examples.tagger.Tagger;
 
 import org.apache.uima.jcas.JCas;
 
-import org.werti.uima.types.annot.SentenceAnnotation;
-import org.werti.uima.types.annot.Token;
-
 public class LingPipeTagger extends JCasAnnotator_ImplBase implements Tagger {
 
 	public void process(JCas cas) {
-		final AnnotationIndex sentIndex = cas.getAnnotationIndex(SentenceAnnotation.type);
-		final AnnotationIndex toknIndex = cas.getAnnotationIndex(Token.type);
-
-		final Iterator<SentenceAnnotation> sit = sentIndex.iterator();
-
-/*
- *                while (sit.hasNext()) {
- *                        sentence.clear();
- *                        tlist.clear();
- *                        final SentenceAnnotation sa = sit.next();
- *                        Iterator<Token> tit = toknIndex.subiterator(sa);
- *
- *                        // fill sentence
- *                        while (tit.hasNext()) {
- *                                final Token t = tit.next();
- *                                tlist.add(t);
- *                                sentence.add(new TaggedWord(t.getCoveredText()));
- *                        }
- *
- *                        assert true: tlist.size() == sentence.size();
- *                        final int size = tlist.size();
- *                        for (int i = 0; i < size; i++) {
- *                                final Token t = tlist.get(i);
- *                                t.setTag(sentence.get(i).tag());
- *                        }
- *                }
- */
+	
 	}
 
 	public void initialize(UimaContext context) {
-
-	}
-
-	public class WertiHandler implements TagHandler {
-
-		public void handle (String[] tokens, String[] ws, String[] tags) {
-			assert true: tokens.length == tags.length;
-
-			for (int ii = 0; ii < tokens.length; ii++) {
-				
-			}
-		}
+	
 	}
 }

### 2008-07-03 src/org/werti/uima/ae/PTBTagger.java

@@ -48,7 +48,7 @@ public class PTBTagger extends JCasAnnotator_ImplBase implements Tagger {
 			getContext().getLogger().log(Level.INFO, "URL.toString(): "
 					+ rurl);
 			getContext().getLogger().log(Level.INFO, "Constructing tagger...");
-			MaxentTagger.init(resource);
+			MaxentTagger.init( "/home/aleks/src/werti/src/org/werti/resources/models/ptbtagger/bidirectional-wsj-0-18.tagger");
 			getContext().getLogger().log(Level.INFO, "Done.");
 		} catch (Exception e) {
 			context.getLogger().log(Level.SEVERE, "Failed to initialize tagger!");

### 2008-07-03 src/org/werti/uima/ae/SimpleTokenizer.java

@@ -40,9 +40,7 @@ public class SimpleTokenizer extends JCasAnnotator_ImplBase {
 			for (int i = 1; i < span.length; i++) {
 				if ((Character.getType(span[i]) != Character.getType(span[i-1]))
 				||   Character.getType(span[i]) == Character.DIRECTIONALITY_WHITESPACE
-				||   span[i] == '.'
-				&&  (span[i] == '-' && span[i-1] != Character.DIRECTIONALITY_WHITESPACE)
-				) {
+				||   span[i] == '.') {
 					final Token t = new Token(cas);
 					t.setBegin(lskew);
 					t.setEnd((lskew = gskew + i));

### 2008-07-03 src/org/werti/uima/enhancer/FIBEnhancer.java

@@ -1,0 +1,137 @@
+package org.werti.uima.enhancer;
+
+import java.util.Iterator;
+
+import org.apache.uima.analysis_component.JCasAnnotator_ImplBase;
+
+import org.apache.uima.cas.FSIndex;
+
+import org.apache.uima.jcas.JCas;
+
+import org.apache.uima.jcas.cas.IntegerArray;
+import org.apache.uima.jcas.cas.StringArray;
+
+import org.apache.uima.util.Level;
+
+import org.werti.uima.types.Enhancement;
+
+import org.werti.uima.types.annot.Token;
+
+
+public class FIBEnhancer extends JCasAnnotator_ImplBase {
+	private static final String TAG = "NN";
+
+	private static int id = 0;
+
+	private static String get_id(int a) {
+		return "WERTi-span-" + (id+a);
+	}
+
+	public void process(JCas cas) {
+		final FSIndex textIndex = cas.getAnnotationIndex(Token.type);
+		final Iterator<Token> tit = textIndex.iterator();
+
+		Token t = tit.next();
+
+		{//begin form
+			final Enhancement e_start = new Enhancement(cas);
+			e_start.setBegin(t.getBegin());
+			e_start.setEnd(t.getBegin());
+			final StringArray  sa = new StringArray(cas, 1);
+			final IntegerArray ia = new IntegerArray(cas, 1);
+
+			sa.set(0,
+					"<form action=\"javascript:void(null)\">"
+					+ "<script type=\"text/javascript\">"
+					+ "function fieldAct(id,token,usertoken,spanid) {"
+					+ "if (token == usertoken)	{"
+					+ "document.getElementById(spanid).innerHTML = token ; "
+					+ "document.getElementById(spanid).style.color = 'green';"
+					+ "document.getElementById(spanid).style.fontWeight = 'bold';"
+					+ "}"
+					+ "else {"
+					+ "document.getElementById(id).style.color = 'red';"
+					+ "document.getElementById(id).style.fontWeight = 'bold';"
+					+ "}"
+					+ "}"
+					+ "</script>"
+					+ "<form action=\"javascript:void(null)\">"
+					+ "<script type=\"text/javascript\">"
+					+ "function fieldAct(id,token,usertoken,spanid) {"
+					+ "if (token == usertoken)	{"
[…]

### 2008-07-03 src/org/werti/uima/enhancer/PoSEnhancer.java

@@ -59,40 +59,6 @@ public class PoSEnhancer extends JCasAnnotator_ImplBase {
 		return "WERTi-span-" + id;
 	}
 
-	@SuppressWarnings("unchecked")
-	private static void fibnew(JCas cas, String[] tags, UimaContext context) {
-		final FSIndex textIndex = cas.getAnnotationIndex(Token.type);
-		final Iterator<Token> tit = textIndex.iterator();
-
-		Token t = tit.next();
-
-		iteratetokens: while (tit.hasNext()) {
-			if (t.getTag() == null) {
-				context.getLogger().log(Level.WARNING,
-						"Encountered token with NULL tag");
-				tit.next();
-				continue iteratetokens;
-			}
-			if (arrayContains(t.getTag(), tags)) {
-				final Enhancement e = new Enhancement(cas);
-				e.setBegin(t.getBegin());
-				e.setEnd(t.getEnd());
-				final StringArray  sa = new StringArray(cas, 2);
-				final IntegerArray ia = new IntegerArray(cas, 2);
-
-				id++;
-				sa.set(0, "<span id=\"" + get_id() + "\">");
-				sa.set(1, "</span>");
-
-				ia.set(0, e.getBegin());
-				ia.set(1, e.getEnd());
-				e.setEnhancement_list(sa);
-				e.setIndex_list(ia);
-				e.addToIndexes();
-			}
-			t = tit.next();
-		}
-	}
 	// put annotations for FIB enhancement in the CAS
 	@SuppressWarnings("unchecked")
 	private static void fib(JCas cas, String[] tags, UimaContext context) {
@@ -274,7 +240,7 @@ public class PoSEnhancer extends JCasAnnotator_ImplBase {
 			t = tit.next();
 		}
 	}
-
+	
 	// does an array of Strings contain a given String?
 	private static boolean arrayContains(String data, String[] sa) {
 		for (String s:sa) {

### 2008-07-03 src/org/werti/Interface.java
First migration commit.
Updated README. Removed all path specs except for the ones in the
descriptors. The descriptors are now really part of the webapp. Maybe
that's not good. They should at least be hidden.

@@ -1,180 +1,0 @@
-package org.werti;
-
-import java.io.*;
-
-import java.util.Iterator;
-import java.util.Map;
-
-import java.util.logging.*;
-import java.util.logging.Level;
-
-import javax.servlet.*;
-
-import javax.servlet.http.*;
-
-import lib.html.Net;
-
-import org.apache.uima.UIMAFramework;
-
-import org.apache.uima.analysis_engine.AnalysisEngine;
-
-import org.apache.uima.cas.FSIndex;
-
-import org.apache.uima.jcas.JCas;
-
-import org.apache.uima.jcas.cas.IntegerArray;
-import org.apache.uima.jcas.cas.StringArray;
-
-import org.apache.uima.resource.ResourceSpecifier;
-
-import org.apache.uima.util.InvalidXMLException;
-import org.apache.uima.util.XMLInputSource;
-
-import org.werti.uima.types.Enhancement;
-
-/**
- * It will, according to its arguments, call the appropriate classes that
- * are needed to fulfill a specific task.
- */
-
-public class Interface extends HttpServlet {
-	static final long serialVersionUID = 0;
-	private static final String PREFIX = "/var/local/werti/resources/descriptors/";
-	private static final String ENHNCE = "/home/aleks/src/werti/desc/enhancers/PoSEnhancer.xml";
-
-	private static final Logger log = Logger.getLogger("org.werti");
-
-	@SuppressWarnings("unchecked")
-	public void doGet(HttpServletRequest request, HttpServletResponse response)
-		throws IOException, ServletException {
-		//DEBUG
-		log.setLevel(Level.ALL);
-
-		// Get parameters
-		final String[] tags = request.getParameter("tags").split("\\s*,\\s*");
-		final String tagger = request.getParameter("tagger");
-		final String termOrURL = request.getParameter("termOrUrl");
-		final String tokenizer = request.getParameter("tokenizer");
-		final String enhance = request.getParameter("enhance");
-
-		final String baseurl = Net.find_baseurl(termOrURL);
-		log.fine("Fetching: " + termOrURL + "; baseurl = " + baseurl);
-
-		// log this event's arguments
-		final Map<String,String[]> args = request.getParameterMap();
-		for (final Map.Entry<String,String[]> e: args.entrySet()) {
-			final String[] vs = e.getValue();
-			String r = "";
[…]

### 2008-07-03 src/org/werti/RequestReuters.java

@@ -1,98 +1,0 @@
-package org.werti;
-
-import java.io.*;
-
-import java.net.MalformedURLException;
-
-import java.util.Enumeration;
-
-import java.util.logging.*;
-
-import javax.servlet.*;
-
-import javax.servlet.http.*;
-
-import lib.html.Net;
-
-public class RequestReuters extends HttpServlet {
-	static final long serialVersionUID = 0;
-	private static final Logger log = Logger.getLogger("org.werti");
-
-	/**
-	 * Fetch the article, replace some html-elements so the site doesn't display completely
-	 * awkward and print it to the screen.
-	 *
-	 * This could probably be done cleaner with DOM, but using regexps is arguably more 
-	 * efficient.
-	 *
-	 * The Regexps must be refined to not overgenerate. Currently the last two are especially
-	 * dangerous. They're going to match a whole lot of stuff that might not be their job.
-	 * For example, in the middle of a path something like var='value'/somewhere (although this
-	 * is unlikely.
-	 *
-	 * This method is still very flaky and should probably be refactored to exist in a UIMAn
-	 * context.
-	 */
-	public void doGet(HttpServletRequest request, HttpServletResponse response)
-		throws IOException, ServletException {
-		log.setLevel(Level.FINEST);
-
-		final String article = request.getParameter("url");
-		final String baseurl = Net.find_baseurl(article);
-		final PrintWriter out = response.getWriter();
-		final BufferedReader in = Net.fetch(article);
-
-		response.setContentType("text/html");
-
-		log.info("Fetched " + article);
-		log.info("baseurl: " + baseurl);
-
-		if (!in.ready()) {
-			log.severe("Input stream to " + article + " not ready!");
-		}
-
-		try {
-			//String b = "";
-			while (in.ready()) {
-				final String line = in.readLine();
-				out.print( (line
-				      + "\n"
-				      // FIXME doesn't account for relative paths
-					).replaceAll("href=\"/", "href=\"" + baseurl
-					).replaceAll("background=\"", "background=\"" + baseurl
-					).replaceAll("src=\"/", "src=\"" + baseurl
-					).replaceAll("@import\\s*\"/", "@import \"" + baseurl
-					//).replaceAll("\"/", "\"" + baseurl // FIXME: this is dirty...
-					//).replaceAll("'/", "'" + baseurl // FIXME: this is dirty...
-					));
-			}
[…]

### 2008-07-03 src/org/werti/RequestWiki.java

@@ -1,75 +1,0 @@
-package org.werti;
-
-import java.io.*;
-
-import java.net.MalformedURLException;
-
-import java.util.Enumeration;
-
-import java.util.logging.*;
-
-import javax.servlet.*;
-
-import javax.servlet.http.*;
-
-import lib.html.Net;
-
-public class RequestWiki extends HttpServlet {
-	static final long serialVersionUID = 0;
-	private static final Logger log = Logger.getLogger("org.werti");
-
-	public void doGet(HttpServletRequest request, HttpServletResponse response)
-		throws IOException, ServletException {
-		log.setLevel(Level.FINEST);
-		response.setHeader("host", "en.wikipedia.org");
-		response.setContentType("text/html");
-		PrintWriter out = response.getWriter();
-		final String article = request.getParameter("wikiquery");
-		log.info("Fetched " + article);
-		try {
-			logResponseHeader(response);
-			logRequestHeader(request);
-			String b = "";
-			final BufferedReader in = Net.fetch(wikify(article));
-			while (in.ready()) {
-				b += (in.readLine() + "\n"
-						).replaceAll("href=\"/", "href=\"" + "http://en.wikipedia.org/"
-						).replaceAll("src=\"/", "src=\"" + "http://en.wikipedia.org/"
-						).replaceAll("@import\\s*\"/", "@import \"" + "http://en.wikipedia.org/"
-						).replaceAll("\"/", "\"" + "http://en.wikipedia.org/")
-						;
-			}
-			out.print(b);
-		} catch (MalformedURLException mue) {
-			log.log(Level.SEVERE, "Malformed URL", mue);
-		} catch (IOException ioe) {
-			log.log(Level.SEVERE, "Wrong content?", ioe);
-		}
-	}
-
-	private static void logRequestHeader(HttpServletRequest r) {
-		log.fine("ContextPath: " + r.getContextPath());
-		final Enumeration<String> e = r.getHeaderNames();
-		while (e.hasMoreElements()) {
-			final String s = e.nextElement();
-			log.fine("Header: " + s + "\n" + r.getHeader(s));
-		}
-
-
-	}
-
-	private static void logResponseHeader(HttpServletResponse r) {
-
-	}
-
-	private static String wikify(String term) {
-		return "http://en.wikipedia.org/wiki/" + term.replace(" ", "_");
-	}
-
-	public void doPost(HttpServletRequest request, HttpServletResponse response)
[…]

### 2008-07-03 src/org/werti/client/WERTiConstants.java

@@ -8,11 +8,4 @@ public interface WERTiConstants extends Constants {
 	 * Names of the themes available.
 	 */
 	String[] THEMES = { "dark", "light", "orange" };
-
-	/**
-	 * Location of the Interface class to pass the URL to.
-	 */
-	String UIMA_INTERFACE_LOCATION = "/werti/Interface";
-
-	String DESCRIPTOR_LOCATION = "/var/local/resources/werti/descriptors";
 }

### 2008-07-03 src/org/werti/server/WERTiServiceImpl.java

@@ -37,10 +37,9 @@ import org.werti.client.WERTiService;
 import org.werti.uima.types.Enhancement;
 
 public class WERTiServiceImpl extends RemoteServiceServlet implements WERTiService {
-	private static final String PREFIX = "/var/local/resources/werti/descriptors/";
+	private static final String PREFIX = "desc";
 	private static final String ENHNCE = PREFIX + "enhancers/PoSEnhancer.xml";
 	private static final String OPERTR = PREFIX + "operators/";
-
 
 	// maximum amount of of ms to wait for a web-page to load
 	private static final int MAX_WAIT = 1000 * 10;

### 2008-07-05 src/org/werti/client/Application.java
Making progress. Now using semi-static UI
Started UI implementation from scratch. What a mess

@@ -1,272 +1,0 @@
-package org.werti.client;
-
-import com.google.gwt.core.client.GWT;
-
-import com.google.gwt.user.client.Window;
-import com.google.gwt.user.client.WindowResizeListener;
-
-import com.google.gwt.user.client.rpc.AsyncCallback;
-import com.google.gwt.user.client.rpc.ServiceDefTarget;
-
-import com.google.gwt.user.client.ui.Button;
-import com.google.gwt.user.client.ui.CheckBox;
-import com.google.gwt.user.client.ui.ClickListener;
-import com.google.gwt.user.client.ui.Composite;
-import com.google.gwt.user.client.ui.FlowPanel;
-import com.google.gwt.user.client.ui.HTML;
-import com.google.gwt.user.client.ui.HorizontalPanel;
-import com.google.gwt.user.client.ui.RadioButton;
-import com.google.gwt.user.client.ui.TabPanel;
-import com.google.gwt.user.client.ui.TextBox;
-import com.google.gwt.user.client.ui.VerticalPanel;
-import com.google.gwt.user.client.ui.Widget;
-
-public class Application extends Composite implements WindowResizeListener {
-
-	public class CRadioButton extends RadioButton implements isUseful {
-		private String canonicalValue;
-
-		public String getCanonicalValue() { return canonicalValue; }
-
-		public CRadioButton(String group, String text, String cv) {
-			super(group, text);
-			this.canonicalValue = cv;
-		}
-	}
-
-	public class CCheckBox extends CheckBox implements isUseful {
-		private String canonicalValue;
-
-		public String getCanonicalValue() { return canonicalValue; }
-
-		public CCheckBox(String text, String cv) {
-			super(text);
-			this.canonicalValue = cv;
-		}
-	}
-
-	public interface isUseful {
-		public boolean isChecked();
-		public String getCanonicalValue();
-	}
-
-	private static final String[] enhancementMethods = { "clr", "ask", "fib" };
-	private static final String[] enhancementNames = { "Colorize"
-			, "Click on the right word"
-			, "Fill in the blanks" };
-	private String defaultEnhancement = "clr";
-
-	private static final String[] posTags = { "NN", "IN", "DT" };
-	private static final String[] posNames = { "Nouns", "Prepositions", "Determiners" };
[…]

### 2008-07-05 src/org/werti/client/Enhancements.java

@@ -1,62 +1,0 @@
-package org.werti.client;
-
-import com.google.gwt.core.client.EntryPoint;
-
-import com.google.gwt.user.client.DOM;
-import com.google.gwt.user.client.Element;
-
-import com.google.gwt.user.client.ui.HTML;
-import com.google.gwt.user.client.ui.KeyboardListener;
-import com.google.gwt.user.client.ui.RootPanel;
-import com.google.gwt.user.client.ui.TextBox;
-import com.google.gwt.user.client.ui.Widget;
-
-public class Enhancements implements EntryPoint {
-	public static final String PREFIX = "WERTi-span-";
-	Element e;
-	RootPanel trp;
-	public void onModuleLoad() {
-		for (int i = 0; ; i++) {
-			e = DOM.getElementById(PREFIX+i);
-			trp = RootPanel.get(PREFIX+i);
-			if (e == null) { break; }
-			final String word = e.getNodeValue();
-			e.setNodeValue("");
-			TextBox tb = new TextBox();
-			tb.setWidth((10*word.length())+"pt");
-		}
-	}
-
-	private class BlankListener implements KeyboardListener {
-		TextBox next;
-		String word;
-		String id;
-		public BlankListener(String word, String id) {
-			this.id = id;
-			this.word = word;
-		}
-
-		public void setNext(TextBox next) {
-			this.next = next;
-		}
-		
-		public void onKeyDown(Widget w, char key, int i) {
-		}
-
-		public void onKeyPress(Widget w, char key, int i) {
-			if (w instanceof TextBox) {
-				TextBox tb = (TextBox) w;
-				if (tb.getText().equals(word)) {
-					w.setVisible(false);
-					RootPanel.get(id).add(new HTML("<font color=\"#00FF00\">"+word+"</font>"));
-					if (next != null) {
-						next.setFocus(true);
-					}
-				} 
-			}
-		}
-
-		public void onKeyUp(Widget w, char key, int i) {
-		}
-	}
-}

### 2008-07-05 src/org/werti/client/EnhancementsService.java

@@ -1,7 +1,0 @@
-package org.werti.client;
-
-import com.google.gwt.user.client.rpc.RemoteService;
-
-public interface EnhancementsService extends RemoteService {
-
-}

### 2008-07-05 src/org/werti/client/EnhancementsServiceAsync.java

@@ -1,5 +1,0 @@
-package org.werti.client;
-
-public interface EnhancementsServiceAsync extends EnhancementsService {
-
-}

### 2008-07-05 src/org/werti/client/WERTi.java

@@ -1,20 +1,13 @@
 package org.werti.client;
 
 import com.google.gwt.core.client.EntryPoint;
-import com.google.gwt.core.client.GWT;
-
-import com.google.gwt.dom.client.Document;
-import com.google.gwt.dom.client.HeadElement;
-import com.google.gwt.dom.client.LinkElement;
 
 import com.google.gwt.user.client.ui.Button;
 import com.google.gwt.user.client.ui.ClickListener;
-import com.google.gwt.user.client.ui.Composite;
-import com.google.gwt.user.client.ui.DialogBox;
 import com.google.gwt.user.client.ui.HTML;
-import com.google.gwt.user.client.ui.Label;
+import com.google.gwt.user.client.ui.HorizontalPanel;
 import com.google.gwt.user.client.ui.RootPanel;
-import com.google.gwt.user.client.ui.VerticalPanel;
+import com.google.gwt.user.client.ui.TextBox;
 import com.google.gwt.user.client.ui.Widget;
 
 /**
@@ -22,83 +15,39 @@ import com.google.gwt.user.client.ui.Widget;
  */
 public class WERTi implements EntryPoint {
 
-	private Label styleTester;
-
-	private Composite app;
+	final HTML status = new HTML("Ready.");
 
 	/**
 	 * This is the entry point method.
 	 */
 	public void onModuleLoad() {
-		// The root panel.
-		VerticalPanel mainPanel = new VerticalPanel();
-		mainPanel.addStyleName("widePanel");
-		mainPanel.setHorizontalAlignment(VerticalPanel.ALIGN_CENTER);
-
-		// Create a widget to test when style sheets are loaded
-		styleTester = new HTML("<div class=\"topLeftInner\"></div>");
-		styleTester.setStyleName("gwt-DecoratorPanel");
-		styleTester.getElement().getStyle().setProperty("position", "absolute");
-		styleTester.getElement().getStyle().setProperty("visibility", "hidden");
-		styleTester.getElement().getStyle().setProperty("display", "inline");
-		styleTester.getElement().getStyle().setPropertyPx("padding", 0);
-		styleTester.getElement().getStyle().setPropertyPx("top", 0);
-		styleTester.getElement().getStyle().setPropertyPx("left", 0);
-		RootPanel.get().add(styleTester);
-
-		// Create the constants
-		WERTiConstants constants = (WERTiConstants) GWT.create(WERTiConstants.class);
-
-		// Create the User Interface
[…]

### 2008-07-05 src/org/werti/client/WERTiConstants.java

@@ -1,11 +1,0 @@
-package org.werti.client;
-
-import com.google.gwt.i18n.client.Constants;
-
-public interface WERTiConstants extends Constants {
-
-	/**
-	 * Names of the themes available.
-	 */
-	String[] THEMES = { "dark", "light", "orange" };
-}

### 2008-07-05 src/org/werti/client/WERTiService.java

@@ -1,7 +1,0 @@
-package org.werti.client;
-
-import com.google.gwt.user.client.rpc.RemoteService;
-
-public interface WERTiService extends RemoteService {
-	public String process(String[] pipeline, String[] tags, String url, String enhance);
-}

### 2008-07-05 src/org/werti/client/WERTiServiceAsync.java

@@ -1,8 +1,0 @@
-package org.werti.client;
-
-import com.google.gwt.user.client.rpc.AsyncCallback;
-
-public interface WERTiServiceAsync {
-	@SuppressWarnings("unchecked")
-	public void process(String[] pipeline, String[] tags, String url, String enhance, AsyncCallback callback);
-}

### 2008-07-05 src/org/werti/client/WERTiUI.java

@@ -1,73 +1,0 @@
-package org.werti.client;
-
-import com.google.gwt.user.client.WindowResizeListener;
-
-import com.google.gwt.user.client.ui.Composite;
-import com.google.gwt.user.client.ui.HTML;
-import com.google.gwt.user.client.ui.SimplePanel;
-import com.google.gwt.user.client.ui.VerticalPanel;
-import com.google.gwt.user.client.ui.Widget;
-
-public class WERTiUI extends Composite implements WindowResizeListener {
-
-	private static final String STYLE_PREFIX = "WERTi";
-	int windowWidth;
-
-	VerticalPanel topPanel;
-
-	/**
-	 * Content wrapper. Put stuff here.
-	 */
-	private SimplePanel contentWrapper;
-
-	/**
-	 * Constructs the layout and widegts of the application.
-	 */
-	public WERTiUI() {
-		mkTopPanel();
-	}
-
-	/**
-	 * Create top panel containing account status
-	 */
-	private void mkTopPanel() {
-		topPanel = new VerticalPanel();
-		topPanel.setStyleName(STYLE_PREFIX + "-top"); 
-		Label foo = "You are not logged in.";
-		topPanel.add(foo);
-	}
-
-	@Override protected void onLoad() {
-		super.onLoad();
-		Window.addWindowResizeListener(this);
-		onWindowResized(Window.getClientWidth(), Window.getClientHeight());
-	}
-
-	@Override protected void onUnload() {
-		super.onUnload();
-		Window.removeWindowResizeListener(this);
-		windowWidth = -1;
-	}
-
-	@Override public void onWindowResized(int width, int height) {
-		if (width == windowWidth) {
-			return;
-		}
-		windowWidth = width;
-	}
-
-	/// Utility Methods \\\
-
-	/**
-	 * Convenience method.
-	 *
-	 * Adds the {@link Widget} or an &amp;nbsp;-entity if the parameter is null.
-	 */
-	public void addWidget(Widget content) {
-		if (content == null) {
-			contentWrapper.setWidget(new HTML("&nbsp;"));
-		} else {
-			contentWrapper.setWidget(content);
-		}
-	}
-}

### 2008-07-05 src/org/werti/server/WERTiServiceImpl.java

@@ -1,240 +1,0 @@
-package org.werti.server;
-
-import java.io.BufferedReader;
-import java.io.FileWriter;
-import java.io.IOException;
-import java.io.InputStreamReader;
-
-import java.net.MalformedURLException;
-import java.net.URL;
-import java.net.URLConnection;
-
-import java.util.Iterator;
-
-import java.util.logging.Level;
-import java.util.logging.Logger;
-
-import com.google.gwt.user.server.rpc.RemoteServiceServlet;
-
-import org.apache.uima.UIMAFramework;
-
-import org.apache.uima.analysis_engine.AnalysisEngine;
-
-import org.apache.uima.cas.FSIndex;
-
-import org.apache.uima.jcas.JCas;
-
-import org.apache.uima.jcas.cas.IntegerArray;
-import org.apache.uima.jcas.cas.StringArray;
-
-import org.apache.uima.resource.ResourceSpecifier;
-
-import org.apache.uima.util.InvalidXMLException;
-import org.apache.uima.util.XMLInputSource;
-
-import org.werti.client.WERTiService;
-
-import org.werti.uima.types.Enhancement;
-
-public class WERTiServiceImpl extends RemoteServiceServlet implements WERTiService {
-	private static final String PREFIX = "desc";
-	private static final String ENHNCE = PREFIX + "enhancers/PoSEnhancer.xml";
-	private static final String OPERTR = PREFIX + "operators/";
-
-	// maximum amount of of ms to wait for a web-page to load
-	private static final int MAX_WAIT = 1000 * 10;
-
-	private static final Logger log = Logger.getLogger("org.werti");
-
-	public static final long serialVersionUID = 0;
-
-	public String process(String[] pipeline, String[] tags, String url, String enhance) {
-		//DEBUG
-		log.setLevel(Level.ALL);
-
-		log.fine("Arguments, pipeline:");
-		for (String e:pipeline) {
-			log.fine(e);
-		}
-		log.fine("Arguments, tags");
-		for (String e:tags) {
-			log.fine(e);
-		}
-		log.fine("Arguments, url: "+url);
-
-		String descriptor = "";
-		for (String e:pipeline) {
-			descriptor += e + "-";
-		}
-		descriptor = OPERTR + descriptor.substring(0,descriptor.length()-1) + ".xml";
-		log.config("Calling descriptor " + descriptor);
-
-		log.fine("Fetching site " + url);
-		final Fetcher fetcher = new Fetcher(url);
-		fetcher.start();
-
-		try {
[…]

### 2008-07-05 www/org.werti.Enhancements/org.werti.Enhancements.nocache.js

@@ -1,11 +1,0 @@
-function org_werti_Enhancements(){var l='',B='" for "gwt:onLoadErrorFn"',z='" for "gwt:onPropertyErrorFn"',Ab='"><\/script>',n='/',kb='554FA1957D8CA44CB270E3FA5CD81A79.cache.html',zb='<script id="',wb="<script>org_werti_Enhancements.onInjectionDone('org.werti.Enhancements')<\/script>",v='=',jb='AAD58EA97F2A158608157BADE6401B29.cache.html',ib='B74223BC92A149A9B6B82BF77E29B9F0.cache.html',y='Bad handler "',sb='DOMContentLoaded',Bb='SCRIPT',yb='__gwt_marker_org.werti.Enhancements',o='base',q='clear.cache.gif',u='content',db='gecko',eb='gecko1_8',nb='gwt.hybrid',lb='gwt/standard/standard.css',A='gwt:onLoadErrorFn',w='gwt:onPropertyErrorFn',t='gwt:property',rb='head',hb='hosted.html?org_werti_Enhancements',qb='href',bb='ie6',tb='iframe',p='img',ub="javascript:''",mb='link',r='meta',gb='moduleRequested',ab='msie',s='name',D='opera',m='org.werti.Enhancements',vb='position:absolute;width:0;height:0;border:none',ob='rel',F='safari',xb='selectionDone',cb='selectionStart',x='startup',pb='stylesheet',fb='unknown',C='user.agent',E='webkit';var Db=window,k=document,fc=Db.external,Cb=Db.__gwtstatsEvent?function(a,b,c,d){Db.__gwtstatsEvent(a,b,c,d)}:null,sc,ic,cc,bc=l,lc={},vc=[],rc=[],ac=[],oc,qc;Cb&&Cb(m,x,cb,{millis:(new Date()).getTime()});if(!Db.__gwt_stylesLoaded){Db.__gwt_stylesLoaded={}}if(!Db.__gwt_scriptsLoaded){Db.__gwt_scriptsLoaded={}}function hc(){try{return fc&&(fc.gwtOnLoad&&Db.location.search.indexOf(nb)==-1)}catch(a){return false}}
[…]

### 2008-07-05 www/org.werti.WERTi/org.werti.WERTi.nocache.js

@@ -1,11 +1,11 @@
-function org_werti_WERTi(){var l='',B='" for "gwt:onLoadErrorFn"',z='" for "gwt:onPropertyErrorFn"',Db='"><\/script>',n='/',mb='123F8ECD63B00246DD298394A9F81FE0.cache.html',lb='31730C6CDEA21B8DBACAECF03D5A56E3.cache.html',kb='3A0FDE4B723F2740F0F7EE6B5EC50B5F.cache.html',jb='40ECB8FEA3690FC56BFBE965FCF917E8.cache.html',ib='46B06708921D05517CB18D90DE745FA9.cache.html',Cb='<script id="',Ab="<script>org_werti_WERTi.onInjectionDone('org.werti.WERTi')<\/script>",v='=',y='Bad handler "',vb='DOMContentLoaded',Eb='SCRIPT',ub='WERTi.css',Bb='__gwt_marker_org.werti.WERTi',o='base',q='clear.cache.gif',u='content',db='gecko',eb='gecko1_8',nb='gwt.hybrid',ob='gwt/standard/standard.css',A='gwt:onLoadErrorFn',w='gwt:onPropertyErrorFn',t='gwt:property',tb='head',hb='hosted.html?org_werti_WERTi',sb='href',bb='ie6',wb='iframe',p='img',xb="javascript:''",pb='link',r='meta',gb='moduleRequested',ab='msie',s='name',D='opera',m='org.werti.WERTi',zb='position:absolute;width:0;height:0;border:none',qb='rel',F='safari',yb='selectionDone',cb='selectionStart',x='startup',rb='stylesheet',fb='unknown',C='user.agent',E='webkit';var ac=window,k=document,ic=ac.external,Fb=ac.__gwtstatsEvent?function(a,b,c,d){ac.__gwtstatsEvent(a,b,c,d)}:null,vc,lc,fc,ec=l,oc={},yc=[],uc=[],dc=[],rc,tc;Fb&&Fb(m,x,cb,{millis:(new Date()).getTime()});if(!ac.__gwt_stylesLoaded){ac.__gwt_stylesLoaded={}}if(!ac.__gwt_scriptsLoaded){ac.__gwt_scriptsLoaded={}}function kc(){try{return ic&&(ic.gwtOnLoad&&ac.location.search.indexOf(nb)==-1)}catch(a){return false}}
[…]

### 2008-07-06 src/org/werti/WERTiContext.java
Modularization. WERTiContext. Properties. Langs.
A lot of work on modularizing everything and making it more portable to
ther systems. That'll teach me to do this right from the start next
time.

Using .properties files now. Migration not! complete, need to migrate
the analysis engines, too, so they use the context.

Added benefit: we might get i18n support for the analysis process
easily this way.

@@ -1,0 +1,120 @@
+package org.werti;
+
+import java.io.IOException;
+import java.io.InputStream;
+import java.io.ObjectInputStream;
+
+import java.net.MalformedURLException;
+import java.net.URL;
+
+import java.util.Properties;
+
+import javax.servlet.ServletContext;
+
+import edu.stanford.nlp.tagger.maxent.MaxentTagger;
+
+import org.apache.commons.logging.Log;
+import org.apache.commons.logging.LogFactory;
+
+import org.apache.uima.examples.tagger.trainAndTest.ModelGeneration;
+
+public class WERTiContext {
+	private static final String PROPS = "/WERTi.properties";
+	private static final Log log =
+		LogFactory.getLog(WERTiContext.class);
+
+	// Burn, memory, burn!
+	private static ServletContext servlet;
+	private static MaxentTagger ptbtagger_en;
+	private static MaxentTagger ptbtagger_de;
+	private static MaxentTagger ptbtagger_ar;
+	private static MaxentTagger ptbtagger_zh;
+	private static ModelGeneration hmmtagger_en;
+	private static ModelGeneration hmmtagger_de;
+
+	private static final Properties p = new Properties();
+
+	public WERTiContext(final ServletContext servlet) {
+		WERTiContext.servlet = servlet;
+		InputStream is = servlet.getResourceAsStream(PROPS);
+		try {
+			p.load(is);
+		} catch (IOException ioe) {
+			log.fatal("Unable to load properties!",ioe);
+		}
+	}
+
+	// return the appropriate tagger reference for the language
+	private static MaxentTagger get_ptbtagger(final String lang) {
+		if (lang.equals("de")) {
+			return WERTiContext.ptbtagger_de;
+		} else if (lang.equals("zh")) {
+			return WERTiContext.ptbtagger_zh;
+		} else if (lang.equals("ar")) {
+			return WERTiContext.ptbtagger_ar;
+		} else {
+			return WERTiContext.ptbtagger_en;
+		}
+	}
+	// return the appropriate tagger reference for the language
+	private static ModelGeneration get_hmmtagger(final String lang) {
+		if (lang.equals("de")) {
+			return WERTiContext.hmmtagger_de;
+		} else  {
+			return WERTiContext.hmmtagger_en;
+		}
+	}
+
+	/**
+	 * Gets the ptbtagger for this instance.
+	 *
[…]

### 2008-07-06 src/org/werti/client/WERTi.java

@@ -1,13 +1,25 @@
 package org.werti.client;
 
 import com.google.gwt.core.client.EntryPoint;
+import com.google.gwt.core.client.GWT;
+
+import com.google.gwt.user.client.rpc.AsyncCallback;
+import com.google.gwt.user.client.rpc.ServiceDefTarget;
 
 import com.google.gwt.user.client.ui.Button;
+import com.google.gwt.user.client.ui.CheckBox;
 import com.google.gwt.user.client.ui.ClickListener;
+import com.google.gwt.user.client.ui.DisclosureEvent;
+import com.google.gwt.user.client.ui.DisclosureHandler;
+import com.google.gwt.user.client.ui.DisclosurePanel;
 import com.google.gwt.user.client.ui.HTML;
 import com.google.gwt.user.client.ui.HorizontalPanel;
+import com.google.gwt.user.client.ui.Label;
+import com.google.gwt.user.client.ui.RadioButton;
 import com.google.gwt.user.client.ui.RootPanel;
+import com.google.gwt.user.client.ui.TabPanel;
 import com.google.gwt.user.client.ui.TextBox;
+import com.google.gwt.user.client.ui.VerticalPanel;
 import com.google.gwt.user.client.ui.Widget;
 
 /**
@@ -24,7 +36,37 @@ public class WERTi implements EntryPoint {
 		final Button submitURL = new Button("Submit URL");
 		submitURL.addClickListener(new ClickListener() {
 			public void onClick(Widget w) {
-				status.setHTML("Not implemented yet");
+				final String[] data = collectData();
+				final String method = data[0];
+				final String lang = data[1];
+				final String[] tags = new String[data.length-2];
+				for (int n = 2; n < data.length; n++) {
+					tags[n-2] = data[n];
+				}
+				final WERTiServiceAsync service = 
+					(WERTiServiceAsync) GWT.create(WERTiService.class);
+				final ServiceDefTarget target = (ServiceDefTarget) service;
+				target.setServiceEntryPoint(GWT.getModuleBaseURL()+"/UIMAProcessor");
+
+				@SuppressWarnings("unchecked")
+				AsyncCallback callback = new AsyncCallback() {
+					public void onFailure(Throwable reason) {
+						StringBuilder sb = new StringBuilder();
+						for (StackTraceElement ste:reason.getStackTrace()) {
+							sb.append(ste.toString() + "<br />");
+						}
+						status.setHTML("Error processing " 
[…]

### 2008-07-06 src/org/werti/client/WERTiService.java

@@ -1,0 +1,7 @@
+package org.werti.client;
+
+import com.google.gwt.user.client.rpc.RemoteService;
+
+public interface WERTiService extends RemoteService {
+	public String process(String method, String language, String[] tags, String url);
+}

### 2008-07-06 src/org/werti/client/WERTiServiceAsync.java

@@ -1,0 +1,8 @@
+package org.werti.client;
+
+import com.google.gwt.user.client.rpc.AsyncCallback;
+
+public interface WERTiServiceAsync {
+	@SuppressWarnings("unchecked")
+	public void process(String method, String language, String[] tags, String url, AsyncCallback callback);
+}

### 2008-07-06 src/org/werti/server/WERTiServiceImpl.java

@@ -1,0 +1,175 @@
+package org.werti.server;
+
+import java.io.FileWriter;
+import java.io.IOException;
+
+import java.net.MalformedURLException;
+import java.net.URL;
+
+import java.util.Iterator;
+
+import com.google.gwt.user.server.rpc.RemoteServiceServlet;
+
+import lib.html.Fetcher;
+
+import org.apache.commons.logging.Log;
+import org.apache.commons.logging.LogFactory;
+
+import org.apache.uima.UIMAFramework;
+
+import org.apache.uima.analysis_engine.AnalysisEngine;
+
+import org.apache.uima.cas.FSIndex;
+
+import org.apache.uima.jcas.JCas;
+
+import org.apache.uima.jcas.cas.IntegerArray;
+import org.apache.uima.jcas.cas.StringArray;
+
+import org.apache.uima.resource.ResourceSpecifier;
+
+import org.apache.uima.util.InvalidXMLException;
+import org.apache.uima.util.XMLInputSource;
+
+import org.werti.client.WERTiService;
+
+import org.werti.uima.types.Enhancement;
+
+public class WERTiServiceImpl extends RemoteServiceServlet implements WERTiService {
+	private static final Log log = LogFactory.getLog(WERTiServiceImpl.class);
+
+	private static final String PREFIX = "/desc/";
+	private static final String ENHNCE = PREFIX + "enhancers/PoSEnhancer.xml";
+	private static final String OPERATORS = PREFIX + "operators/";
+
+	// maximum amount of of ms to wait for a web-page to load
+	private static final int MAX_WAIT = 1000 * 10;
+
+
+	public static final long serialVersionUID = 0;
+
+	public String process(String method, String language, String[] tags, String url) {
+		//DEBUG
+		log.debug("Arguments, pipeline:");
+		log.debug("Arguments, tags");
+		for (String e:tags) {
+			log.debug(e);
+		}
+		log.debug("Arguments, url: "+url);
+
+		for (Object path:getServletContext().getResourcePaths("/")) {
+			log.error("Path: "+path);
+		}
+
+		final URL descriptor;
+		try {
+			descriptor = getServletContext().getResource(OPERATORS + "ptb-ptb-hil.xml");
+		} catch (MalformedURLException murle) {
+			log.error("The Url is invalid!", murle);
+			throw new RuntimeException("Invalid URL!");
+		}
+
+		log.debug("Fetching site " + url);
[…]

### 2008-07-06 src/org/werti/uima/ae/PTBTagger.java

@@ -42,13 +42,10 @@ public class PTBTagger extends JCasAnnotator_ImplBase implements Tagger {
 		super.initialize(context);
 		try {
 			final String resource = (String) context.getConfigParameterValue(pModel);
-			getContext().getLogger().log(Level.INFO, "Resource file should be: "
-					+ resource);
-			final URL rurl = ClassLoader.getSystemResource(resource);
-			getContext().getLogger().log(Level.INFO, "URL.toString(): "
-					+ rurl);
-			getContext().getLogger().log(Level.INFO, "Constructing tagger...");
-			MaxentTagger.init( "/home/aleks/src/werti/src/org/werti/resources/models/ptbtagger/bidirectional-wsj-0-18.tagger");
+			getContext().getLogger().log(Level.INFO, "Resource file should be: " + resource);
+			final URL url = ClassLoader.getSystemClassLoader().getResource("jndi:/WERTi"+resource);
+			getContext().getLogger().log(Level.INFO, "Constructing tagger... url: "+url);
+			MaxentTagger.init(resource);
 			getContext().getLogger().log(Level.INFO, "Done.");
 		} catch (Exception e) {
 			context.getLogger().log(Level.SEVERE, "Failed to initialize tagger!");

### 2008-07-06 www/org.werti.WERTi/org.werti.WERTi.nocache.js

@@ -1,11 +1,11 @@
-function org_werti_WERTi(){var l='',B='" for "gwt:onLoadErrorFn"',z='" for "gwt:onPropertyErrorFn"',Db='"><\/script>',n='/',mb='31CB8029C4813D7751A1AA5FD336960F.cache.html',kb='55EF1760610F7AEA3876D1AF101E4F28.cache.html',jb='5A0A267C38B7829D1A59A9314B7B5C65.cache.html',ib='5D90049144BCD6CE1EC3EAD8F163911B.cache.html',lb='87D0793201661FD637935D5691CF9981.cache.html',Cb='<script id="',Ab="<script>org_werti_WERTi.onInjectionDone('org.werti.WERTi')<\/script>",v='=',y='Bad handler "',vb='DOMContentLoaded',Eb='SCRIPT',Bb='__gwt_marker_org.werti.WERTi',o='base',q='clear.cache.gif',u='content',db='gecko',eb='gecko1_8',nb='gwt.hybrid',ob='gwt/standard/standard.css',A='gwt:onLoadErrorFn',w='gwt:onPropertyErrorFn',t='gwt:property',tb='head',hb='hosted.html?org_werti_WERTi',sb='href',bb='ie6',wb='iframe',p='img',xb="javascript:''",pb='link',r='meta',gb='moduleRequested',ab='msie',s='name',D='opera',m='org.werti.WERTi',zb='position:absolute;width:0;height:0;border:none',qb='rel',F='safari',yb='selectionDone',cb='selectionStart',x='startup',rb='stylesheet',fb='unknown',C='user.agent',E='webkit',ub='werti.css';var ac=window,k=document,ic=ac.external,Fb=ac.__gwtstatsEvent?function(a,b,c,d){ac.__gwtstatsEvent(a,b,c,d)}:null,vc,lc,fc,ec=l,oc={},yc=[],uc=[],dc=[],rc,tc;Fb&&Fb(m,x,cb,{millis:(new Date()).getTime()});if(!ac.__gwt_stylesLoaded){ac.__gwt_stylesLoaded={}}if(!ac.__gwt_scriptsLoaded){ac.__gwt_scriptsLoaded={}}function kc(){try{return ic&&(ic.gwtOnLoad&&ac.location.search.indexOf(nb)==-1)}catch(a){return false}}
[…]

### 2008-07-06 src/org/werti/WERTiContext.java
Context should be usable. Not tested yet.

@@ -20,11 +20,11 @@ import org.apache.uima.examples.tagger.trainAndTest.ModelGeneration;
 
 public class WERTiContext {
 	private static final String PROPS = "/WERTi.properties";
-	private static final Log log =
-		LogFactory.getLog(WERTiContext.class);
+	private static final Log log = LogFactory.getLog(WERTiContext.class);
 
-	// Burn, memory, burn!
 	private static ServletContext servlet;
+
+	// Burn, memory, burn! FIXME: this needs more testing!
 	private static MaxentTagger ptbtagger_en;
 	private static MaxentTagger ptbtagger_de;
 	private static MaxentTagger ptbtagger_ar;
@@ -41,6 +41,7 @@ public class WERTiContext {
 			p.load(is);
 		} catch (IOException ioe) {
 			log.fatal("Unable to load properties!",ioe);
+			throw new RuntimeException("I don't kow where the taggers are!", ioe);
 		}
 	}
 
@@ -56,6 +57,7 @@ public class WERTiContext {
 			return WERTiContext.ptbtagger_en;
 		}
 	}
+
 	// return the appropriate tagger reference for the language
 	private static ModelGeneration get_hmmtagger(final String lang) {
 		if (lang.equals("de")) {
@@ -68,9 +70,10 @@ public class WERTiContext {
 	/**
 	 * Gets the ptbtagger for this instance.
 	 *
+	 * @param lang The two letter language code
 	 * @return The ptbtagger.
 	 */
-	public MaxentTagger getPtbtagger (final String lang) {
+	public static MaxentTagger getPtbtagger (final String lang) {
 		MaxentTagger ptbtagger = get_ptbtagger(lang);
 		if (ptbtagger == null) {
 			final String ptbloc = p.getProperty("ptbtagger.base")
@@ -96,9 +99,10 @@ public class WERTiContext {
 	/**
 	 * Gets the hmmtagger for this instance.
 	 *
+	 * @param lang The two-letter language code
 	 * @return The hmmtagger.
 	 */
-	public ModelGeneration getHmmtagger(final String lang) {
+	public static ModelGeneration getHmmtagger(final String lang) {
 		ModelGeneration hmmtagger = get_hmmtagger(lang);
 		if (hmmtagger == null) {
 			final String hmmloc = p.getProperty("hmmtagger.base")
@@ -111,8 +115,10 @@ public class WERTiContext {
 				hmmtagger = (ModelGeneration) ois.readObject();
[…]

### 2008-07-06 src/org/werti/server/WERTiServiceImpl.java

@@ -31,6 +31,8 @@ import org.apache.uima.resource.ResourceSpecifier;
 import org.apache.uima.util.InvalidXMLException;
 import org.apache.uima.util.XMLInputSource;
 
+import org.werti.WERTiContext;
+
 import org.werti.client.WERTiService;
 
 import org.werti.uima.types.Enhancement;
@@ -45,11 +47,13 @@ public class WERTiServiceImpl extends RemoteServiceServlet implements WERTiServi
 	// maximum amount of of ms to wait for a web-page to load
 	private static final int MAX_WAIT = 1000 * 10;
 
+	private static WERTiContext context; 
 
 	public static final long serialVersionUID = 0;
 
 	public String process(String method, String language, String[] tags, String url) {
 		//DEBUG
+		context = new WERTiContext(getServletContext());
 		log.debug("Arguments, pipeline:");
 		log.debug("Arguments, tags");
 		for (String e:tags) {

### 2008-07-06 src/org/werti/server/WERTiServiceImpl.java
Reworked Exception handling and Logging in TAEs.
Also tweaked the tagger initialization code. Init is no take care of by
WERTiContext. Let's hope it'll work.

@@ -51,7 +51,8 @@ public class WERTiServiceImpl extends RemoteServiceServlet implements WERTiServi
 
 	public static final long serialVersionUID = 0;
 
-	public String process(String method, String language, String[] tags, String url) {
+	public String process(String method, String language, String[] tags, String url) 
+		throws MalformedURLException {
 		//DEBUG
 		context = new WERTiContext(getServletContext());
 		log.debug("Arguments, pipeline:");
@@ -66,12 +67,7 @@ public class WERTiServiceImpl extends RemoteServiceServlet implements WERTiServi
 		}
 
 		final URL descriptor;
-		try {
-			descriptor = getServletContext().getResource(OPERATORS + "ptb-ptb-hil.xml");
-		} catch (MalformedURLException murle) {
-			log.error("The Url is invalid!", murle);
-			throw new RuntimeException("Invalid URL!");
-		}
+		descriptor = getServletContext().getResource(OPERATORS + "ptb-ptb-hil.xml");
 
 		log.debug("Fetching site " + url);
 		final Fetcher fetcher = new Fetcher(url);

### 2008-07-06 src/org/werti/uima/ae/HMMTagger.java

@@ -1,10 +1,5 @@
 package org.werti.uima.ae;
 
-import java.io.FileInputStream;
-import java.io.IOException;
-import java.io.InputStream;
-import java.io.ObjectInputStream;
-
 import java.util.ArrayList;
 import java.util.Iterator;
 import java.util.List;
@@ -14,8 +9,6 @@ import org.apache.uima.UimaContext;
 import org.apache.uima.analysis_component.JCasAnnotator_ImplBase;
 
 import org.apache.uima.analysis_engine.AnalysisEngineProcessException;
-
-import org.apache.uima.analysis_engine.annotator.AnnotatorConfigurationException;
 
 import org.apache.uima.cas.text.AnnotationIndex;
 
@@ -28,7 +21,7 @@ import org.apache.uima.jcas.JCas;
 
 import org.apache.uima.resource.ResourceInitializationException;
 
-import org.apache.uima.util.Level;
+import org.werti.WERTiContext;
 
 import org.werti.uima.types.annot.SentenceAnnotation;
 import org.werti.uima.types.annot.Token;
@@ -43,8 +36,7 @@ public class HMMTagger extends JCasAnnotator_ImplBase implements Tagger {
 	private int N;
 
 	// model generation
-	private static final String pModel = "MODEL_LOCATION";
-	private ModelGeneration model;
+	private final ModelGeneration model = WERTiContext.getHmmtagger("en");
 
 	/**
 	 * Initializes the HMMTagger with a model supplied by the configuration-resource
@@ -54,50 +46,7 @@ public class HMMTagger extends JCasAnnotator_ImplBase implements Tagger {
 	 */
 	public void initialize(final UimaContext context) throws ResourceInitializationException {
 		super.initialize(context);
-		try {
-			this.N = (Integer) context.getConfigParameterValue(pN);
-			this.model = get_model(context);
-		} catch (AnnotatorConfigurationException ace) {
-			throw new ResourceInitializationException(ace);
-		} catch (Exception e) {
-			throw new ResourceInitializationException(e);
-		}
-	}
-
-	// initialize the model from context
-	private static ModelGeneration get_model(final UimaContext context) 
-		throws AnnotatorConfigurationException {
-		return get_model(context, null);
-	}
-
-	// initialize the model
-	private static ModelGeneration get_model(final UimaContext context, final String loc)
-		throws AnnotatorConfigurationException {
-		final InputStream model;
-		try {
[…]

### 2008-07-06 src/org/werti/uima/ae/HTMLAnnotator.java

@@ -2,11 +2,12 @@ package org.werti.uima.ae;
 
 // import type
 
+import org.apache.commons.logging.Log;
+import org.apache.commons.logging.LogFactory;
+
 import org.apache.uima.analysis_component.JCasAnnotator_ImplBase;
 
 import org.apache.uima.jcas.JCas;
-
-import org.apache.uima.util.Level;
 
 import org.werti.uima.types.annot.HTML;
 
@@ -16,7 +17,11 @@ import org.werti.uima.types.annot.HTML;
  * Properties include 'closing', 'irrelevant' and the 'tag_name'. Also their absolute
  * position in the CAS.
  */
+
 public class HTMLAnnotator extends JCasAnnotator_ImplBase {
+	private static final Log log =
+		LogFactory.getLog(HTMLAnnotator.class);
+
 	private static final char[] TAG_NAME_DELMTR = { ' ', '\t', '\n', '\r', '>'};
 
 	/**
@@ -26,8 +31,7 @@ public class HTMLAnnotator extends JCasAnnotator_ImplBase {
 	 * position in the CAS.
 	 */
 	public void process(JCas cas) {
-		getContext().getLogger().log(Level.INFO,
-				"Starting HTML tag recognition");
+		log.info("Starting HTML tag recognition");
 		final String s = cas.getDocumentText();
 		int tstart = 0;
 		int tend = 0;
@@ -36,13 +40,11 @@ public class HTMLAnnotator extends JCasAnnotator_ImplBase {
 			tag.setBegin(tstart);
 			tag.setEnd(tend = (s.indexOf('>', tstart) + 1));
 
-			getContext().getLogger().log(Level.FINEST,
-					"tstart = " + tstart + "; tend = " + tend);
+			log.debug("tstart = " + tstart + "; tend = " + tend);
 
 			final String tname = find_tname(s.substring(tstart, tend));
 
-			getContext().getLogger().log(Level.FINEST,
-					"Looking at tag " + tname);
+			log.debug("Looking at tag " + tname);
 
 			tstart = tend;
 
@@ -62,8 +64,7 @@ public class HTMLAnnotator extends JCasAnnotator_ImplBase {
 			tag.addToIndexes();
 
 		}
-		getContext().getLogger().log(Level.INFO,
-				"Finished HTML tag recognition");
+		log.info("Finished HTML tag recognition");
 	}
 
 	// skips ahead and marks irrelevant tags

### 2008-07-06 src/org/werti/uima/ae/LingPipeTokenizer.java

@@ -2,7 +2,8 @@ package org.werti.uima.ae;
 
 import java.util.Iterator;
 
-import com.aliasi.corpus.TagHandler;
+import org.apache.commons.logging.Log;
+import org.apache.commons.logging.LogFactory;
 
 import org.apache.uima.analysis_component.JCasAnnotator_ImplBase;
 
@@ -10,12 +11,13 @@ import org.apache.uima.cas.FSIndex;
 
 import org.apache.uima.jcas.JCas;
 
-import org.apache.uima.util.Level;
-
 import org.werti.uima.types.annot.RelevantText;
 import org.werti.uima.types.annot.Token;
 
 public class LingPipeTokenizer extends JCasAnnotator_ImplBase {
+	private static final Log log =
+		LogFactory.getLog(LingPipeTokenizer.class);
+
 
 	/**
 	 * Go through all relevant text areas in the RelevantText-AnnotationIndex and annotate them
@@ -26,7 +28,7 @@ public class LingPipeTokenizer extends JCasAnnotator_ImplBase {
 	 */
 	@SuppressWarnings("unchecked")
 	public void process(JCas cas) {
-		getContext().getLogger().log(Level.INFO, "Starting tokenization process.");
+		log.info("Starting tokenization");
 		final FSIndex textIndex = cas.getAnnotationIndex(RelevantText.type);
 		final Iterator<RelevantText> tit = textIndex.iterator();
 
@@ -50,7 +52,7 @@ public class LingPipeTokenizer extends JCasAnnotator_ImplBase {
 				}
 			}
 		}
-		getContext().getLogger().log(Level.INFO, "Finished tokenization process.");
+		log.info("Finished tokenization");
 	}
 
 }

### 2008-07-06 src/org/werti/uima/ae/PTBTagger.java

@@ -1,7 +1,5 @@
 package org.werti.uima.ae;
 
-import java.net.URL;
-
 import java.util.ArrayList;
 import java.util.Iterator;
 import java.util.List;
@@ -9,11 +7,14 @@ import java.util.List;
 import edu.stanford.nlp.ling.Sentence;
 import edu.stanford.nlp.ling.TaggedWord;
 
-import edu.stanford.nlp.tagger.maxent.*;
+import edu.stanford.nlp.tagger.maxent.MaxentTagger;
 
-import org.apache.uima.UimaContext;
+import org.apache.commons.logging.Log;
+import org.apache.commons.logging.LogFactory;
 
 import org.apache.uima.analysis_component.JCasAnnotator_ImplBase;
+
+import org.apache.uima.analysis_engine.AnalysisEngineProcessException;
 
 import org.apache.uima.cas.text.AnnotationIndex;
 
@@ -21,76 +22,53 @@ import org.apache.uima.examples.tagger.Tagger;
 
 import org.apache.uima.jcas.JCas;
 
-import org.apache.uima.resource.ResourceInitializationException;
-
-import org.apache.uima.util.Level;
+import org.werti.WERTiContext;
 
 import org.werti.uima.types.annot.SentenceAnnotation;
 import org.werti.uima.types.annot.Token;
 
 
 public class PTBTagger extends JCasAnnotator_ImplBase implements Tagger {
-	
-	/*
-	 * Parameter definitions
-	 */
+	private static final Log log =
+		LogFactory.getLog(PTBTagger.class);
 
-	// Model file
-	private static final String pModel = "MODEL_LOCATION";
-
-	public void initialize(UimaContext context) throws ResourceInitializationException {
-		super.initialize(context);
-		try {
-			final String resource = (String) context.getConfigParameterValue(pModel);
-			getContext().getLogger().log(Level.INFO, "Resource file should be: " + resource);
-			final URL url = ClassLoader.getSystemClassLoader().getResource("jndi:/WERTi"+resource);
-			getContext().getLogger().log(Level.INFO, "Constructing tagger... url: "+url);
-			MaxentTagger.init(resource);
-			getContext().getLogger().log(Level.INFO, "Done.");
-		} catch (Exception e) {
-			context.getLogger().log(Level.SEVERE, "Failed to initialize tagger!");
-			throw new RuntimeException("No tagger, no game.", e);
-		}
-	}
[…]

### 2008-07-06 src/org/werti/uima/ae/PTBTokenizer.java

@@ -6,18 +6,22 @@ import java.util.Iterator;
 
 import edu.stanford.nlp.ling.Word;
 
+import org.apache.commons.logging.Log;
+import org.apache.commons.logging.LogFactory;
+
 import org.apache.uima.analysis_component.JCasAnnotator_ImplBase;
 
 import org.apache.uima.cas.FSIndex;
 
 import org.apache.uima.jcas.JCas;
 
-import org.apache.uima.util.Level;
-
 import org.werti.uima.types.annot.RelevantText;
 import org.werti.uima.types.annot.Token;
 
 public class PTBTokenizer extends JCasAnnotator_ImplBase {
+	private static final Log log =
+		LogFactory.getLog(PTBTokenizer.class);
+
 
 	/**
 	 * Go through all relevant text areas in the RelevantText-AnnotationIndex and annotate them
@@ -26,8 +30,9 @@ public class PTBTokenizer extends JCasAnnotator_ImplBase {
 	 * We only set the CAS-relative Begin and End, but also set the Word-Property of Token for now. This may
 	 * change in the future for efficiency reasons.
 	 */
+	@SuppressWarnings("unchecked")
 	public void process(JCas cas) {
-		getContext().getLogger().log(Level.INFO, "Starting tokenization process.");
+		log.info("Starting Tokenization");
 		final FSIndex textIndex = cas.getAnnotationIndex(RelevantText.type);
 		final Iterator<RelevantText> tit = textIndex.iterator();
 
@@ -52,6 +57,6 @@ public class PTBTokenizer extends JCasAnnotator_ImplBase {
 				t.addToIndexes();
 			}
 		}
-		getContext().getLogger().log(Level.INFO, "Finished tokenization process.");
+		log.info("Finished Tokenization");
 	}
 }

### 2008-07-06 src/org/werti/uima/ae/SentenceBoundaryDetector.java

@@ -3,13 +3,11 @@ package org.werti.uima.ae;
 import java.util.Arrays;
 import java.util.HashSet;
 import java.util.Iterator;
-import java.util.NoSuchElementException;
 import java.util.Set;
 
-import edu.stanford.nlp.ling.Sentence;
-import edu.stanford.nlp.ling.TaggedWord;
 
-import edu.stanford.nlp.tagger.maxent.MaxentTagger;
+import org.apache.commons.logging.Log;
+import org.apache.commons.logging.LogFactory;
 
 import org.apache.uima.analysis_component.JCasAnnotator_ImplBase;
 
@@ -17,13 +15,14 @@ import org.apache.uima.cas.FSIndex;
 
 import org.apache.uima.jcas.JCas;
 
-import org.apache.uima.util.Level;
-
 import org.werti.uima.types.annot.SentenceAnnotation;
 import org.werti.uima.types.annot.Token;
 
 
 public class SentenceBoundaryDetector extends JCasAnnotator_ImplBase {
+	private static final Log log =
+		LogFactory.getLog(SentenceBoundaryDetector.class);
+
 	private static final Set<String> sentenceBoundaries = 
 		new HashSet<String>(Arrays.asList(new String[]{".", "!", "?"}));
 	private static final Set<String> sentenceBoundaryFollowers =
@@ -37,8 +36,9 @@ public class SentenceBoundaryDetector extends JCasAnnotator_ImplBase {
 	 *
 	 * @param cas The Cas the Tokens come from and the sentences go to.
 	 */
+	@SuppressWarnings("unchecked")
 	public void process(JCas cas) {
-		getContext().getLogger().log(Level.INFO, "Starting sentence boundary detection.");
+		log.info("Starting sentence boundary detection.");
 
 		final FSIndex textIndex = cas.getAnnotationIndex(Token.type);
 		final Iterator<Token> tit = textIndex.iterator();
@@ -48,9 +48,8 @@ public class SentenceBoundaryDetector extends JCasAnnotator_ImplBase {
 		Token t;
 		while (tit.hasNext()) {
 			t = tit.next();
-			getContext().getLogger().log(Level.FINEST, "Looking at token: " + t);
+			log.debug("Looking at token: " + t);
 
-			final String w = t.getCoveredText();
 			SentenceAnnotation sa = new SentenceAnnotation(cas);
 			sa.setBegin(t.getBegin());
 
[…]

### 2008-07-06 src/org/werti/uima/ae/SimpleTokenizer.java

@@ -2,18 +2,22 @@ package org.werti.uima.ae;
 
 import java.util.Iterator;
 
+import org.apache.commons.logging.Log;
+import org.apache.commons.logging.LogFactory;
+
 import org.apache.uima.analysis_component.JCasAnnotator_ImplBase;
 
 import org.apache.uima.cas.FSIndex;
 
 import org.apache.uima.jcas.JCas;
 
-import org.apache.uima.util.Level;
-
 import org.werti.uima.types.annot.RelevantText;
 import org.werti.uima.types.annot.Token;
 
 public class SimpleTokenizer extends JCasAnnotator_ImplBase {
+	private static final Log log =
+		LogFactory.getLog(SimpleTokenizer.class);
+
 
 	/**
 	 * Go through all relevant text areas in the RelevantText-AnnotationIndex and annotate them
@@ -24,7 +28,7 @@ public class SimpleTokenizer extends JCasAnnotator_ImplBase {
 	 */
 	@SuppressWarnings("unchecked")
 	public void process(JCas cas) {
-		getContext().getLogger().log(Level.INFO, "Starting tokenization process.");
+		log.info("Starting tokenization process.");
 		final FSIndex textIndex = cas.getAnnotationIndex(RelevantText.type);
 		final Iterator<RelevantText> tit = textIndex.iterator();
 
@@ -48,6 +52,6 @@ public class SimpleTokenizer extends JCasAnnotator_ImplBase {
 				}
 			}
 		}
-		getContext().getLogger().log(Level.INFO, "Finished tokenization process.");
+		log.info("Finished tokenization process.");
 	}
 }

### 2008-07-06 src/org/werti/uima/ae/relevance/GenericRelevanceAnnotator.java

@@ -6,13 +6,16 @@ import java.util.Stack;
 
 import java.util.regex.Pattern;
 
+import org.apache.commons.logging.Log;
+import org.apache.commons.logging.LogFactory;
+
 import org.apache.uima.analysis_component.JCasAnnotator_ImplBase;
+
+import org.apache.uima.analysis_engine.AnalysisEngineProcessException;
 
 import org.apache.uima.cas.FSIndex;
 
 import org.apache.uima.jcas.JCas;
-
-import org.apache.uima.util.Level;
 
 import org.werti.uima.types.annot.HTML;
 import org.werti.uima.types.annot.RelevantText;
@@ -26,6 +29,9 @@ import org.werti.uima.types.annot.RelevantText;
  * Sometimes this will mark garbage. It might prove hard to actually fix this, though.
  */
 public class GenericRelevanceAnnotator extends JCasAnnotator_ImplBase {
+	private static final Log log =
+		LogFactory.getLog(GenericRelevanceAnnotator.class);
+
 
 	private static final Pattern whiteSpacePattern = Pattern.compile("^\\s*$");
 
@@ -36,16 +42,16 @@ public class GenericRelevanceAnnotator extends JCasAnnotator_ImplBase {
 	 * The 'relevance'-notion is a primitive one. We just don't care about stuff that is
 	 * enclosed in, say <i>&lt;script&gt;</i> tags.
 	 */
-	public void process(JCas cas) {
-		getContext().getLogger().log(Level.INFO,
-				"Starting relevance annotation");
+	@SuppressWarnings("unchecked")
+	public void process(JCas cas) throws AnalysisEngineProcessException {
+		log.info("Starting relevance annotation");
 		final Stack<String> tags = new Stack<String>();
 		final FSIndex tagIndex = cas.getAnnotationIndex(HTML.type);
 		final Iterator<HTML> tit = tagIndex.iterator();
 		HTML tag = tit.next();
 		if (tag == null) {
-			getContext().getLogger().log(Level.SEVERE, 
-					"HTML tag was null while starting to search for relevance.");
+			throw new AnalysisEngineProcessException(
+					new NullPointerException("No Html tags were found!"));
 		}
 
 		// skip ahead to the body
@@ -75,9 +81,7 @@ public class GenericRelevanceAnnotator extends JCasAnnotator_ImplBase {
 				try {
 					while (tags.pop().equals(tname)); // read: until not...
[…]

### 2008-07-06 src/org/werti/uima/enhancer/PoSEnhancer.java

@@ -2,6 +2,9 @@ package org.werti.uima.enhancer;
 
 import java.util.Iterator;
 
+import org.apache.commons.logging.Log;
+import org.apache.commons.logging.LogFactory;
+
 import org.apache.uima.UimaContext;
 
 import org.apache.uima.analysis_component.JCasAnnotator_ImplBase;
@@ -13,26 +16,26 @@ import org.apache.uima.jcas.JCas;
 import org.apache.uima.jcas.cas.IntegerArray;
 import org.apache.uima.jcas.cas.StringArray;
 
-import org.apache.uima.util.Level;
-
 import org.werti.uima.types.Enhancement;
 
 import org.werti.uima.types.annot.Token;
 
 
 public class PoSEnhancer extends JCasAnnotator_ImplBase {
-	@SuppressWarnings("unchecked")
+	private static final Log log =
+		LogFactory.getLog(PoSEnhancer.class);
+
 	public void process(JCas cas) {
-		getContext().getLogger().log(Level.INFO,
-				"Starting enhancement");
+		log.info("Starting enhancement");
 		Object o = getContext().getConfigParameterValue("Tags");
 		final String[] tags;
 		if (o instanceof String[]) {
 			tags = (String[]) o;
-			getContext().getLogger().log(Level.INFO, "Tags: ");
+			final StringBuilder sb = new StringBuilder();
 			for (String s:tags) {
-				getContext().getLogger().log(Level.INFO, s);
+				sb.append(s + " ");
 			}
+			log.debug("Tags: " + sb.toString());
 		} else {
 			throw new RuntimeException("Expected String Array as Paramater. Aborting");
 		}
@@ -49,8 +52,7 @@ public class PoSEnhancer extends JCasAnnotator_ImplBase {
 		else if (method.equals("fib")) fib(cas, tags, getContext());
 		else if (method.equals("ask")) ask(cas, tags, getContext());
 
-		getContext().getLogger().log(Level.INFO,
-				"Finished enhancement");
+		log.info("Finished enhancement");
 	}
 
 	// need thos two to supply JS-annotations with IDs.
@@ -113,8 +115,7 @@ public class PoSEnhancer extends JCasAnnotator_ImplBase {
 		}
 		iteratetokens: while (tit.hasNext()) {
 			if (t.getTag() == null) {
-				context.getLogger().log(Level.WARNING,
-						"Encountered token with NULL tag");
+				log.debug("Encountered token with NULL tag");
[…]

### 2008-07-06 src/org/werti/server/WERTiServiceImpl.java
Cleaned up server side service implementation
Will probably rework the exception code some more still.

@@ -18,6 +18,7 @@ import org.apache.commons.logging.LogFactory;
 import org.apache.uima.UIMAFramework;
 
 import org.apache.uima.analysis_engine.AnalysisEngine;
+import org.apache.uima.analysis_engine.AnalysisEngineProcessException;
 
 import org.apache.uima.cas.FSIndex;
 
@@ -26,6 +27,7 @@ import org.apache.uima.jcas.JCas;
 import org.apache.uima.jcas.cas.IntegerArray;
 import org.apache.uima.jcas.cas.StringArray;
 
+import org.apache.uima.resource.ResourceInitializationException;
 import org.apache.uima.resource.ResourceSpecifier;
 
 import org.apache.uima.util.InvalidXMLException;
@@ -47,86 +49,84 @@ public class WERTiServiceImpl extends RemoteServiceServlet implements WERTiServi
 	// maximum amount of of ms to wait for a web-page to load
 	private static final int MAX_WAIT = 1000 * 10;
 
-	private static WERTiContext context; 
+	public static WERTiContext context;
 
 	public static final long serialVersionUID = 0;
 
-	public String process(String method, String language, String[] tags, String url) 
-		throws MalformedURLException {
-		//DEBUG
+	public String process(String method, String language, String[] tags, String url) {
 		context = new WERTiContext(getServletContext());
-		log.debug("Arguments, pipeline:");
-		log.debug("Arguments, tags");
-		for (String e:tags) {
-			log.debug(e);
-		}
-		log.debug("Arguments, url: "+url);
-
-		for (Object path:getServletContext().getResourcePaths("/")) {
-			log.error("Path: "+path);
-		}
-
 		final URL descriptor;
-		descriptor = getServletContext().getResource(OPERATORS + "ptb-ptb-hil.xml");
+		try { // to load the descriptor
+			descriptor = getServletContext().getResource(OPERATORS + "ptb-ptb-hil.xml");
+		} catch (MalformedURLException murle) {
+			log.fatal("Unrecoverable: Couldn't find aggregate descriptor file!");
+			throw new RuntimeException(murle);
+		}
 
 		log.debug("Fetching site " + url);
 		final Fetcher fetcher = new Fetcher(url);
 		fetcher.start();
 
-		try {
-			// preprocessor
+		final JCas cas;
+		final AnalysisEngine preprocessor, postprocessor;
+
+		try { // to initialize UIMA components
[…]

### 2008-07-06 src/org/werti/client/InitializationException.java
Fixed Client-Server interaction on Exceptions.
Added exception interpretation on client side, corrected exception
generation on server side. Introduced two new checked exceptions for
this.

@@ -1,0 +1,40 @@
+package org.werti.client;
+
+/**
+ * An Exception to be sent by the server to the client when the initialization
+ * of the processing components fails.
+ *
+ * @author Aleksandar Dimitrov
+ */
+
+public class InitializationException extends Exception {
+
+	public static final long serialVersionUID = 10;
+
+	public InitializationException() {
+		super("Very bad. Tell Aleks to fix his code!");
+	}
+
+	/**
+	 * @param message
+	 */
+	public InitializationException(String message) {
+		super(message);
+	}
+
+	/**
+	 * @param arg0
+	 */
+	public InitializationException(Throwable message) {
+		super(message);
+	}
+
+	/**
+	 * @param message
+	 * @param exception
+	 */
+	public InitializationException(String message, Throwable exception) {
+		super(message, exception);
+	}
+
+}

### 2008-07-06 src/org/werti/client/ProcessingException.java

@@ -1,0 +1,40 @@
+package org.werti.client;
+
+/**
+ * An Exception to be sent by the server to the client when the processing
+ * of the page fails.
+ *
+ * @author Aleksandar Dimitrov
+ */
+
+public class ProcessingException extends Exception {
+
+	public static final long serialVersionUID = 10;
+
+	public ProcessingException() {
+		super("Very bad. Tell Aleks to fix his code!");
+	}
+
+	/**
+	 * @param message
+	 */
+	public ProcessingException(String message) {
+		super(message);
+	}
+
+	/**
+	 * @param arg0
+	 */
+	public ProcessingException(Throwable message) {
+		super(message);
+	}
+
+	/**
+	 * @param message
+	 * @param exception
+	 */
+	public ProcessingException(String message, Throwable exception) {
+		super(message, exception);
+	}
+
+}

### 2008-07-06 src/org/werti/client/WERTi.java

@@ -1,9 +1,12 @@
 package org.werti.client;
 
+import java.net.MalformedURLException;
+
 import com.google.gwt.core.client.EntryPoint;
 import com.google.gwt.core.client.GWT;
 
 import com.google.gwt.user.client.rpc.AsyncCallback;
+import com.google.gwt.user.client.rpc.InvocationException;
 import com.google.gwt.user.client.rpc.ServiceDefTarget;
 
 import com.google.gwt.user.client.ui.Button;
@@ -29,9 +32,59 @@ public class WERTi implements EntryPoint {
 
 	final HTML status = new HTML("Ready.");
 
+	private void showError(String message, String execptionMessage, String cause) {
+
+	}
+
+	@SuppressWarnings("unchecked")
+	private class SearchCallback implements AsyncCallback {
+		public void onFailure(Throwable reason) {
+			StringBuilder sb = new StringBuilder();
+			for (StackTraceElement ste:reason.getStackTrace()) {
+				sb.append(ste.toString() + "<br />");
+			}
+			if (reason instanceof InvocationException) {
+				final InvocationException ie = (InvocationException) reason;
+				showError("Failed to contact Server!"
+						, ie.getMessage()
+						, sb.toString());
+			} else if (reason instanceof ProcessingException) {
+				final ProcessingException pe = (ProcessingException) reason;
+				showError("Failed Processing of <a href=\""
+						+ searchBox.getText() + "\">"
+						+ "the requested page.</a>"
+						+ "<br />. "
+						+ "Sorry. Maybe you'd like to try another?"
+						, pe.getMessage()
+						, sb.toString());
+			} else if (reason instanceof InitializationException) {
+				final InitializationException ie = 
+					(InitializationException) reason;
+				showError("Failed to initialize server-side context. "
+						+ "This probably means that one the option"
+						+ "you chose has some problems currently." 
+						+ "Maybe you could try a different option?"
+						, ie.getMessage()
+						, sb.toString());
+			} else if (reason instanceof MalformedURLException) {
+				final MalformedURLException murle = 
+					(MalformedURLException) reason;
+				showError("The URL you've entered seems invalid. "
+						+ "Try another."
+						, murle.getMessage()
+						, sb.toString());
+			}
+		}
+
+		public void onSuccess(Object result) {
[…]

### 2008-07-06 src/org/werti/client/WERTiService.java

@@ -1,7 +1,10 @@
 package org.werti.client;
 
+import java.net.MalformedURLException;
+
 import com.google.gwt.user.client.rpc.RemoteService;
 
 public interface WERTiService extends RemoteService {
-	public String process(String method, String language, String[] tags, String url);
+	public String process(String method, String language, String[] tags, String url)
+		throws ProcessingException, InitializationException, MalformedURLException;
 }

### 2008-07-06 src/org/werti/client/WERTiServiceAsync.java

@@ -1,8 +1,11 @@
 package org.werti.client;
 
+import java.net.MalformedURLException;
+
 import com.google.gwt.user.client.rpc.AsyncCallback;
 
 public interface WERTiServiceAsync {
 	@SuppressWarnings("unchecked")
-	public void process(String method, String language, String[] tags, String url, AsyncCallback callback);
+	public void process(String method, String language, String[] tags, String url, AsyncCallback callback) 
+		throws ProcessingException, InitializationException, MalformedURLException;
 }

### 2008-07-06 src/org/werti/server/WERTiServiceImpl.java

@@ -35,6 +35,8 @@ import org.apache.uima.util.XMLInputSource;
 
 import org.werti.WERTiContext;
 
+import org.werti.client.InitializationException;
+import org.werti.client.ProcessingException;
 import org.werti.client.WERTiService;
 
 import org.werti.uima.types.Enhancement;
@@ -53,14 +55,15 @@ public class WERTiServiceImpl extends RemoteServiceServlet implements WERTiServi
 
 	public static final long serialVersionUID = 0;
 
-	public String process(String method, String language, String[] tags, String url) {
+	public String process(String method, String language, String[] tags, String url) 
+		throws MalformedURLException, InitializationException, ProcessingException {
 		context = new WERTiContext(getServletContext());
 		final URL descriptor;
 		try { // to load the descriptor
 			descriptor = getServletContext().getResource(OPERATORS + "ptb-ptb-hil.xml");
 		} catch (MalformedURLException murle) {
 			log.fatal("Unrecoverable: Couldn't find aggregate descriptor file!");
-			throw new RuntimeException(murle);
+			throw new InitializationException("Couldn't instantiate operator.", murle);
 		}
 
 		log.debug("Fetching site " + url);
@@ -83,13 +86,13 @@ public class WERTiServiceImpl extends RemoteServiceServlet implements WERTiServi
 			postprocessor  = UIMAFramework.produceAnalysisEngine(post_spec);
 		} catch (InvalidXMLException ixmle) {
 			log.fatal("Error initializing XML code. Invalid?", ixmle);
-			throw new RuntimeException("Error initializing XML code. Invalid?", ixmle);
+			throw new InitializationException("Error initializing XML code. Invalid?", ixmle);
 		} catch (ResourceInitializationException rie) {
 			log.fatal("Error initializing resource", rie);
-			throw new RuntimeException("Error initializing resource", rie);
+			throw new InitializationException("Error initializing resource", rie);
 		} catch (IOException ioe) {
 			log.fatal("Error accessing descriptor file", ioe);
-			throw new RuntimeException("Error accessing descriptor file", ioe);
+			throw new InitializationException("Error accessing descriptor file", ioe);
 		}
 		log.debug("Initialized UIMA components.");
 
@@ -101,7 +104,7 @@ public class WERTiServiceImpl extends RemoteServiceServlet implements WERTiServi
 
[…]

### 2008-07-06 src/org/werti/client/URLException.java
Fixed Handling of Errors on Client side.
Now we really have a nice interface! It' just the CSS that sucks, but
eh... someone should do it...

@@ -1,0 +1,40 @@
+package org.werti.client;
+
+/**
+ * An Exception to be sent by the server to the client when the processing
+ * of the page fails.
+ *
+ * @author Aleksandar Dimitrov
+ */
+
+public class URLException extends Exception {
+
+	public static final long serialVersionUID = 10;
+
+	public URLException() {
+		super("Very bad. Tell Aleks to fix his code!");
+	}
+
+	/**
+	 * @param message
+	 */
+	public URLException(String message) {
+		super(message);
+	}
+
+	/**
+	 * @param arg0
+	 */
+	public URLException(Throwable message) {
+		super(message);
+	}
+
+	/**
+	 * @param message
+	 * @param exception
+	 */
+	public URLException(String message, Throwable exception) {
+		super(message, exception);
+	}
+
+}

### 2008-07-06 src/org/werti/client/WERTi.java

@@ -1,7 +1,5 @@
 package org.werti.client;
 
-import java.net.MalformedURLException;
-
 import com.google.gwt.core.client.EntryPoint;
 import com.google.gwt.core.client.GWT;
 
@@ -12,6 +10,7 @@ import com.google.gwt.user.client.rpc.ServiceDefTarget;
 import com.google.gwt.user.client.ui.Button;
 import com.google.gwt.user.client.ui.CheckBox;
 import com.google.gwt.user.client.ui.ClickListener;
+import com.google.gwt.user.client.ui.DialogBox;
 import com.google.gwt.user.client.ui.DisclosureEvent;
 import com.google.gwt.user.client.ui.DisclosureHandler;
 import com.google.gwt.user.client.ui.DisclosurePanel;
@@ -32,8 +31,54 @@ public class WERTi implements EntryPoint {
 
 	final HTML status = new HTML("Ready.");
 
-	private void showError(String message, String execptionMessage, String cause) {
+	private void showError(String message, String exceptionMessage, String cause) {
+		final DialogBox dialogBox = new DialogBox();
+		dialogBox.setText("We encountered an Error!");
+		dialogBox.setAnimationEnabled(true);
 
+		VerticalPanel dialogVPanel = new VerticalPanel();
+		dialogVPanel.setWidth("100%");
+		dialogVPanel.setHorizontalAlignment(VerticalPanel.ALIGN_CENTER);
+
+		final HTML explanation = new HTML(message);
+
+		final DisclosurePanel moreInfo = new DisclosurePanel("More info:");
+		moreInfo.setAnimationEnabled(true);
+		final VerticalPanel moreInfos = new VerticalPanel();
+		final HTML exmes = new HTML(
+				"The message of the exception thrown:<br />" +exceptionMessage);
+		final HTML stacktrace = new HTML(cause);
+		
+		moreInfos.add(exmes);
+		moreInfos.add(stacktrace);
+		moreInfo.add(moreInfos);
+
+		final Button closeButton = new Button("close");
+		closeButton.addClickListener(new ClickListener() {
+			public void onClick(Widget sender) {
+				dialogBox.hide();
+			}
+		});
+
+		final HTML excuse = new HTML("<p>We're sorry this happened. "
+				+ "The error has been logged on server-side. However, if you "
+				+ "feel this really shouldn't have happened, please feel free "
+				+ "to <a href=\"mailto:admtrov@sfs.uni-tuebingen.de\">"
[…]

### 2008-07-06 src/org/werti/client/WERTiService.java

@@ -1,10 +1,8 @@
 package org.werti.client;
 
-import java.net.MalformedURLException;
-
 import com.google.gwt.user.client.rpc.RemoteService;
 
 public interface WERTiService extends RemoteService {
 	public String process(String method, String language, String[] tags, String url)
-		throws ProcessingException, InitializationException, MalformedURLException;
+		throws ProcessingException, InitializationException, URLException;
 }

### 2008-07-06 src/org/werti/client/WERTiServiceAsync.java

@@ -1,11 +1,9 @@
 package org.werti.client;
 
-import java.net.MalformedURLException;
-
 import com.google.gwt.user.client.rpc.AsyncCallback;
 
 public interface WERTiServiceAsync {
 	@SuppressWarnings("unchecked")
 	public void process(String method, String language, String[] tags, String url, AsyncCallback callback) 
-		throws ProcessingException, InitializationException, MalformedURLException;
+		throws ProcessingException, InitializationException, URLException;
 }

### 2008-07-06 src/org/werti/server/WERTiServiceImpl.java

@@ -37,6 +37,7 @@ import org.werti.WERTiContext;
 
 import org.werti.client.InitializationException;
 import org.werti.client.ProcessingException;
+import org.werti.client.URLException;
 import org.werti.client.WERTiService;
 
 import org.werti.uima.types.Enhancement;
@@ -56,7 +57,7 @@ public class WERTiServiceImpl extends RemoteServiceServlet implements WERTiServi
 	public static final long serialVersionUID = 0;
 
 	public String process(String method, String language, String[] tags, String url) 
-		throws MalformedURLException, InitializationException, ProcessingException {
+		throws URLException, InitializationException, ProcessingException {
 		context = new WERTiContext(getServletContext());
 		final URL descriptor;
 		try { // to load the descriptor
@@ -67,7 +68,12 @@ public class WERTiServiceImpl extends RemoteServiceServlet implements WERTiServi
 		}
 
 		log.debug("Fetching site " + url);
-		final Fetcher fetcher = new Fetcher(url);
+		final Fetcher fetcher;
+		try {
+			fetcher = new Fetcher(url);
+		} catch (MalformedURLException murle) {
+			throw new URLException(murle);
+		}
 		fetcher.start();
 
 		final JCas cas;

### 2008-07-06 www/org.werti.WERTi/org.werti.WERTi.nocache.js

@@ -1,11 +1,11 @@
-function org_werti_WERTi(){var l='',B='" for "gwt:onLoadErrorFn"',z='" for "gwt:onPropertyErrorFn"',Db='"><\/script>',n='/',ib='6347FE53C9A7FCCE675F14CA62088FF6.cache.html',lb='7E9D78BDFA90225F89A6B9F328DFB101.cache.html',Cb='<script id="',Ab="<script>org_werti_WERTi.onInjectionDone('org.werti.WERTi')<\/script>",v='=',kb='AA3BF7F49635D19C2159B3684F91A7DA.cache.html',y='Bad handler "',jb='D849887A6EBC92D8751596C5FEF26F35.cache.html',vb='DOMContentLoaded',mb='EF465FFA064822A802EB6B3E88792783.cache.html',Eb='SCRIPT',Bb='__gwt_marker_org.werti.WERTi',o='base',q='clear.cache.gif',u='content',db='gecko',eb='gecko1_8',nb='gwt.hybrid',ob='gwt/standard/standard.css',A='gwt:onLoadErrorFn',w='gwt:onPropertyErrorFn',t='gwt:property',tb='head',hb='hosted.html?org_werti_WERTi',sb='href',bb='ie6',wb='iframe',p='img',xb="javascript:''",pb='link',r='meta',gb='moduleRequested',ab='msie',s='name',D='opera',m='org.werti.WERTi',zb='position:absolute;width:0;height:0;border:none',qb='rel',F='safari',yb='selectionDone',cb='selectionStart',x='startup',rb='stylesheet',fb='unknown',C='user.agent',E='webkit',ub='werti.css';var ac=window,k=document,ic=ac.external,Fb=ac.__gwtstatsEvent?function(a,b,c,d){ac.__gwtstatsEvent(a,b,c,d)}:null,vc,lc,fc,ec=l,oc={},yc=[],uc=[],dc=[],rc,tc;Fb&&Fb(m,x,cb,{millis:(new Date()).getTime()});if(!ac.__gwt_stylesLoaded){ac.__gwt_stylesLoaded={}}if(!ac.__gwt_scriptsLoaded){ac.__gwt_scriptsLoaded={}}function kc(){try{return ic&&(ic.gwtOnLoad&&ac.location.search.indexOf(nb)==-1)}catch(a){return false}}
[…]
